---
title: "BC_Fish_Abun_Fits_2"
format: html
editor: visual
---
# Description

R code that analyzes the relationship between benthic cover and herbivorous fish abundance, and changes in fish abundance with depth. For the benthic cover and herbivorous fish models, benthic cover was partitioned into whether herbivorous fishes potentially used them as habitat or food. 

# Clean up

```{r}
rm(list=ls())
gc()
```

# Library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

## Load csv

```{r}
fishab <- read_csv("Data/relationship_fish_ab_ben_version3.csv",
                           trim_ws = TRUE)
```

## Select relevant benthic and fish columns

```{r}
fishab_2 <- 
  fishab |> 
  mutate(total_octocoral = complex_octocoral + other_octocoral) |> 
  dplyr::select(Site_recode,
                Habitat,
                #Aspect_descriptive,
                Depth_m,
                cropper,
                browser,
                detritivore,
                excavator, 
                scraper,
                Benthic_Complexity,
                turf_algae,
                total_macroalgae,
                total_hard_coral,
                unconsolidated_subs,
                total_octocoral,
                sponge) |> 
  mutate(total_herbs = cropper + browser + detritivore + excavator + scraper,
         Benthic_Complexity = factor(Benthic_Complexity)) |> 
  mutate(Benthic_Complexity = replace(Benthic_Complexity,
                                 Benthic_Complexity == 3.5,
                                 3)) |> 
  filter(Habitat == "outer_reef") # only grabbed sites that were outer reefs
```

# =================

Code from here examines the relationship between benthic cover and herbivorous fishes (overall and for each feeding group)

# TOTAL HERBIVORS

## HABITAT MODEL

### Def formula

```{r}
herbs_form_ab_hab <- bf(total_herbs ~ 
                   Benthic_Complexity +
                  # turf_algae +
                  # total_macroalgae +
                   total_hard_coral + 
                   unconsolidated_subs +
                   total_octocoral +
                  # sponge +
                   (1 | Site_recode), #+
                    #(1 | Habitat_type) +
                    #(1 | Aspect_descriptive),
                 family = negbinomial())
```

### Weakly informed priors

```{r}
herb_priors_v2 <- prior(normal(1.3, 1.5), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1.5), class = "sd")
```

### Prior only model

```{r}
#| cache: true
herbs_prior_ab_hab_mod <- brm(herbs_form_ab_hab,
                    data = fishab_2,
                    prior = herb_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

### Fit the model

```{r}
#| cache: true
herbs_mod_ab_hab <- update(herbs_prior_ab_hab_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

#### MCMC diagnostics

```{r}
# trace
herbs_mod_ab_hab |> mcmc_plot(type = "trace")
# autocorr
herbs_mod_ab_hab |> mcmc_plot(type = "acf_bar")

# rhat
herbs_mod_ab_hab |> mcmc_plot(type = "rhat_hist")

# ess
herbs_mod_ab_hab |> mcmc_plot(type = "neff_hist")
```

#### Residuals

```{r}
herbs_resids_hab <- make_brms_dharma_res(herbs_mod_ab_hab)

# qqplot
herbs_resids_hab |> testUniformity()

# residplot
herbs_resids_hab |> plotResiduals()

# testdisp
herbs_resids_hab |> testDispersion()
```

##### Save ab hab model

```{r}
save(herbs_mod_ab_hab, file = "Model_Output/herbs_mod_ab_hab_ver2.Rdata")
```

## FOOD MODEL

### Def formula

```{r}
herbs_form_ab_food <- bf(total_herbs ~ 
                   #Benthic_Complexity +
                   turf_algae +
                   total_macroalgae +
                   #total_hard_coral + 
                   #unconsolidated_subs +
                   #total_octocoral +
                   sponge +
                   (1 | Site_recode),# +
                    #(1 | Habitat_type) +
                     #(1 | Aspect_descriptive),
                 family = negbinomial())
```

### Prior only model

```{r}
#| cache: true
herbs_prior_food_mod <- brm(herbs_form_ab_food,
                    data = fishab_2,
                    prior = herb_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

### Fit the model

```{r}
#| cache: true
herbs_food_mod <- update(herbs_prior_food_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

#### MCMC diagnostics

```{r}
# trace
herbs_food_mod |> mcmc_plot(type = "trace")
# autocorr
herbs_food_mod |> mcmc_plot(type = "acf_bar")

# rhat
herbs_food_mod |> mcmc_plot(type = "rhat_hist")

# ess
herbs_food_mod |> mcmc_plot(type = "neff_hist")
```

#### Residuals

```{r}
herbs_resid_food_mod <- make_brms_dharma_res(herbs_food_mod)

# qqplot
herbs_resid_food_mod |> testUniformity()

# residplot
herbs_resid_food_mod |> plotResiduals()

# testdisp
herbs_resid_food_mod |> testDispersion()
```

##### Save ab food model

```{r}
save(herbs_food_mod, file = "Model_Output/herbs_food_mod_ver2.Rdata")
```

# CROPPER

## HABITAT MODEL

### Def formula

```{r}
crop_form_hab <- bf(cropper ~ 
                   Benthic_Complexity +
                   #turf_algae +
                   #total_macroalgae +
                   total_hard_coral + 
                   unconsolidated_subs +
                   total_octocoral +
                   #sponge + 
                   (1 | Site_recode),# +
                     #(1 | Habitat_type) +
                     #(1 | Aspect_descriptive),
                 family = negbinomial())
```

### Weakly informed priors

```{r}
crop_priors <- prior(normal(0.7, 1), class = "Intercept") +
  prior(normal(0, 0.7), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

### Prior only model

```{r}
#| cache: true
crop_prior_hab_mod <- brm(crop_form_hab,
                    data = fishab_2,
                    prior = crop_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

### Fit the model

```{r}
#| cache: true
crop_mod_ab_hab <- update(crop_prior_hab_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

#### MCMC diagnostics

```{r}
# trace
crop_mod_ab_hab |> mcmc_plot(type = "trace")
# autocorr
crop_mod_ab_hab |> mcmc_plot(type = "acf_bar")

# rhat
crop_mod_ab_hab |> mcmc_plot(type = "rhat_hist")

# ess
crop_mod_ab_hab |> mcmc_plot(type = "neff_hist")
```

#### Residuals

```{r}
crop_resids_ab_hab <- make_brms_dharma_res(crop_mod_ab_hab)

# qqplot
crop_resids_ab_hab |> testUniformity()

# residplot
crop_resids_ab_hab |> plotResiduals()

# testdisp
crop_resids_ab_hab |> testDispersion()
```

#### Save crop ab hab model

```{r}
save(crop_mod_ab_hab, file = "Model_Output/crop_mod_ab_hab_ver2.Rdata")
```

## FOOD MODEL

### Def formula

```{r}
crop_form_food <- bf(cropper ~ 
              #     Benthic_Complexity +
                   turf_algae +
                   total_macroalgae +
              #     total_hard_coral + 
               #    unconsolidated_subs +
               #    total_octocoral +
                   sponge + 
                   (1 | Site_recode),# +
                #(1 | Habitat_type) +
                #(1 | Aspect_descriptive),
                 family = negbinomial())
```

### Prior only model

```{r}
#| cache: true
crop_prior_food_mod <- brm(crop_form_food,
                    data = fishab_2,
                    prior = crop_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

### Fit the model

```{r}
#| cache: true
crop_food_mod <- update(crop_prior_food_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

#### MCMC diagnostics

```{r}
# trace
crop_food_mod |> mcmc_plot(type = "trace")
# autocorr
crop_food_mod |> mcmc_plot(type = "acf_bar")

# rhat
crop_food_mod |> mcmc_plot(type = "rhat_hist")

# ess
crop_food_mod |> mcmc_plot(type = "neff_hist")
```

#### Residuals

```{r}
crop_resids_hab <- make_brms_dharma_res(crop_food_mod)

# qqplot
crop_resids_hab |> testUniformity()

# residplot
crop_resids_hab |> plotResiduals()

# testdisp
crop_resids_hab |> testDispersion()
```

##### Save crop food model

```{r}
save(crop_food_mod, file = "Data/crop_food_mod_ver2.Rdata")
```

# DETRITIVORES

## HABITAT MODEL

### Def formula

```{r}
det_form_hab <- bf(detritivore ~ 
                    Benthic_Complexity +
                   #turf_algae +
                   #total_macroalgae +
                   total_hard_coral + 
                   unconsolidated_subs +
                   total_octocoral +
                   #sponge + 
                   (1 | Site_recode),# +
                     #(1 | Habitat_type) +
                     #(1 | Aspect_descriptive),
                 family = negbinomial())
```

### Weakly informed priors

```{r}
det_priors <- prior(normal(0.5, 1), class = "Intercept") +
  prior(normal(0, 0.5), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

### Prior only model

```{r}
#| cache: true
det_prior_hab_mod <- brm(det_form_hab,
                    data = fishab_2,
                    prior = det_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

### Fit the model

```{r}
#| cache: true
det_mod_hab <- update(det_prior_hab_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

#### MCMC diagnostics

```{r}
# trace
det_mod_hab |> mcmc_plot(type = "trace")
# autocorr
det_mod_hab|> mcmc_plot(type = "acf_bar")

# rhat
det_mod_hab |> mcmc_plot(type = "rhat_hist")

# ess
det_mod_hab |> mcmc_plot(type = "neff_hist")
```

#### Residuals

```{r}
det_resids_hab <- make_brms_dharma_res(det_mod_hab)

# qqplot
det_resids_hab |> testUniformity()

# residplot
det_resids_hab |> plotResiduals()

# testdisp
det_resids_hab |> testDispersion()
```

##### Save det ab hab model

```{r}
save(det_mod_hab, file = "Model_Output/det_mod_hab_ver2.Rdata")
```

# FOOD MODELS

### Def formula

```{r}
det_form_food <- bf(detritivore ~ 
           #         Benthic_Complexity +
                   turf_algae +
                   total_macroalgae +
               #    total_hard_coral + 
            #       unconsolidated_subs +
                #   total_octocoral +
                  sponge + 
                   (1 | Site_recode),# +
             #(1 | Habitat_type) +
             #(1 | Aspect_descriptive),
                 family = negbinomial())
```

## prior only model

```{r}
#| cache: true
det_prior_food_mod <- brm(det_form_food,
                    data = fishab_2,
                    prior = det_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## fit the model

```{r}
#| cache: true
det_mod_food <- update(det_prior_food_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
det_mod_food |> mcmc_plot(type = "trace")
# autocorr
det_mod_food |> mcmc_plot(type = "acf_bar")

# rhat
det_mod_food |> mcmc_plot(type = "rhat_hist")

# ess
det_mod_food |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
det_food_resids <- make_brms_dharma_res(det_mod_food)

# qqplot
det_food_resids |> testUniformity()

# residplot
det_food_resids |> plotResiduals()

# testdisp
det_food_resids |> testDispersion()
```

# save det ab food model

```{r}
save(det_mod_food, file = "Data/det_mod_food_ver2.Rdata")
```

# SCRAPERS

## HABITAT MODEL

## def formula

```{r}
scra_form_hab <- bf(scraper ~ 
                     Benthic_Complexity +
                   #turf_algae +
                   #total_macroalgae +
                   total_hard_coral + 
                   unconsolidated_subs +
                   total_octocoral +
                   #sponge + 
                   (1 | Site_recode),# +
                     #(1 | Habitat_type) +
                     #(1 | Aspect_descriptive),
                 family = negbinomial())
```

## weakly informed priors

```{r}
scra_priors <- prior(normal(0.1, 0.3), class = "Intercept") +
  prior(normal(0, 0.3), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 0.3), class = "sd")
```

## prior only model

```{r}
#| cache: true
scra_prior_hab_mod <- brm(scra_form_hab,
                    data = fishab_2,
                    prior = scra_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## fit the model

```{r}
#| cache: true
scra_hab_mod <- update(scra_prior_hab_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
scra_hab_mod |> mcmc_plot(type = "trace")
# autocorr
scra_hab_mod |> mcmc_plot(type = "acf_bar")

# rhat
scra_hab_mod  |> mcmc_plot(type = "rhat_hist")

# ess
scra_hab_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
scra_hab_resids <- make_brms_dharma_res(scra_hab_mod)

# qqplot
scra_hab_resids |> testUniformity()

# residplot
scra_hab_resids |> plotResiduals()

# testdisp
scra_hab_resids |> testDispersion()
```

# save det ab food model

```{r}
save(scra_hab_mod, file = "Data/scra_hab_mod_ver2.Rdata")
```

# FOOD MODEL

## def formula

```{r}
scra_form_food <- bf(scraper ~ 
            #         Benthic_Complexity +
                   turf_algae +
                   total_macroalgae +
              #     total_hard_coral + 
             #      unconsolidated_subs +
               #    total_octocoral +
                   sponge + 
                   (1 | Site_recode),# +
              #(1 | Habitat_type) +
              #(1 | Aspect_descriptive),
                 family = negbinomial())
```

## prior only model

```{r}
#| cache: true
scra_prior_food_mod <- brm(scra_form_food,
                    data = fishab_2,
                    prior = scra_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## fit the model

```{r}
#| cache: true
scra_food_mod <- update(scra_prior_food_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
scra_food_mod |> mcmc_plot(type = "trace")
# autocorr
scra_food_mod |> mcmc_plot(type = "acf_bar")

# rhat
scra_food_mod |> mcmc_plot(type = "rhat_hist")

# ess
scra_food_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
scra_food_resids <- make_brms_dharma_res(scra_food_mod)

# qqplot
scra_food_resids |> testUniformity()

# residplot
scra_food_resids |> plotResiduals()

# testdisp
scra_food_resids |> testDispersion()
```

# save det ab food model

```{r}
save(scra_food_mod, file = "Data/scra_food_mod_ver2.Rdata")
```

# =========================

Code form here examines changes in herbivorous fishes with depth

# TOTAL HERBIVORES

## def formula

```{r}
herbs_form_ab_depth <- bf(total_herbs ~ 
                   Depth_m +
                   (1 | Site_recode), #+
                    #(1 | Habitat_type) +
                    #(1 | Aspect_descriptive),
                 family = negbinomial())
```

## weakly informed priors

```{r}
herb_depth_priors_v2 <- prior(normal(2.1, 2.3), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2.3), class = "sd")
```

## prior only model

```{r}
#| cache: true
herbs_prior_ab_depth_mod <- brm(herbs_form_ab_depth,
                    data = fishab_2,
                    prior = herb_depth_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## fit the model

```{r}
#| cache: true
herbs_depthmod <- update(herbs_prior_ab_depth_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
herbs_depthmod |> mcmc_plot(type = "trace")
# autocorr
herbs_depthmod |> mcmc_plot(type = "acf_bar")

# rhat
herbs_depthmod |> mcmc_plot(type = "rhat_hist")

# ess
herbs_depthmod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
herbs_depthresids <- make_brms_dharma_res(herbs_depthmod)

# qqplot
herbs_depthresids |> testUniformity()

# residplot
herbs_depthresids |> plotResiduals()

# testdisp
herbs_depthresids |> testDispersion()
```

# save ab hab model

```{r}
save(herbs_depthmod, file = "Data/herbs_depthmod_ab_ver2.Rdata")
```

# CROPPER

## def formula

```{r}
crop_form_ab_depth <- bf(cropper ~ 
                   Depth_m +
                   (1 | Site_recode), #+
                    #(1 | Habitat_type) +
                    #(1 | Aspect_descriptive),
                 family = negbinomial())
```

## weakly informed priors

```{r}
crop_depth_priors_v2 <- prior(normal(1.5, 1.7), class = "Intercept") +
  prior(normal(0, 0.9), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1.7), class = "sd")
```

## prior only model

```{r}
#| cache: true
crop_prior_ab_depth_mod <- brm(crop_form_ab_depth,
                    data = fishab_2,
                    prior = crop_depth_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
crop_prior_ab_depth_mod |> 
  conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
crops_depthmod <- update(crop_prior_ab_depth_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
crops_depthmod |> mcmc_plot(type = "trace")
# autocorr
crops_depthmod |> mcmc_plot(type = "acf_bar")

# rhat
crops_depthmod |> mcmc_plot(type = "rhat_hist")

# ess
crops_depthmod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
crop_depthresids <- make_brms_dharma_res(crops_depthmod)

# qqplot
crop_depthresids |> testUniformity()

# residplot
crop_depthresids |> plotResiduals()

# testdisp
crop_depthresids |> testDispersion()
```

# save ab hab model

```{r}
save(crops_depthmod, file = "Data/crops_depthmod_ab_ver2.Rdata")
```

# DETRITIVORE

## def formula

```{r}
det_form_ab_depth <- bf(detritivore ~ 
                   Depth_m +
                   (1 | Site_recode), #+
                    #(1 | Habitat_type) +
                    #(1 | Aspect_descriptive),
                 family = negbinomial())
```

## weakly informed priors

```{r}
det_depth_priors_v2 <- prior(normal(0.8, 1.4), class = "Intercept") +
  prior(normal(0, 0.6), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1.4), class = "sd")
```

## prior only model

```{r}
#| cache: true
det_prior_ab_depth_mod <- brm(det_form_ab_depth,
                    data = fishab_2,
                    prior = det_depth_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## fit the model

```{r}
#| cache: true
det_depthmod <- update(det_prior_ab_depth_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
det_depthmod |> mcmc_plot(type = "trace")
# autocorr
det_depthmod |> mcmc_plot(type = "acf_bar")

# rhat
det_depthmod |> mcmc_plot(type = "rhat_hist")

# ess
det_depthmod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
det_depthresids <- make_brms_dharma_res(det_depthmod)

# qqplot
det_depthresids |> testUniformity()

# residplot
det_depthresids |> plotResiduals()

# testdisp
det_depthresids |> testDispersion()
```

# save ab hab model

```{r}
save(det_depthmod, file = "Data/det_depthmod_ab_ver2.Rdata")
```

# SCRAPER

## def formula

```{r}
scra_form_ab_depth <- bf(scraper ~ 
                   Depth_m +
                   (1 | Site_recode), #+
                    #(1 | Habitat_type) +
                    #(1 | Aspect_descriptive),
                 family = negbinomial())
```

## weakly informed priors

```{r}
scra_depth_priors_v2 <- prior(normal(0.2, 1), class = "Intercept") +
  prior(normal(0, 0.2), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

## prior only model

```{r}
#| cache: true
scra_prior_ab_depth_mod <- brm(scra_form_ab_depth,
                    data = fishab_2,
                    prior = scra_depth_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
scra_prior_ab_depth_mod |> 
  conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
scra_depthmod <- update(scra_prior_ab_depth_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
scra_depthmod |> mcmc_plot(type = "trace")
# autocorr
scra_depthmod |> mcmc_plot(type = "acf_bar")

# rhat
scra_depthmod |> mcmc_plot(type = "rhat_hist")

# ess
scra_depthmod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
scra_depthresids <- make_brms_dharma_res(scra_depthmod)

# qqplot
scra_depthresids |> testUniformity()

# residplot
scra_depthresids |> plotResiduals()

# testdisp
scra_depthresids |> testDispersion()
```

# save ab hab model

```{r}
save(scra_depthmod, file = "Data/scra_depthmod_ab_ver2.Rdata")
```
