---
title: "Untitled"
format: html
editor: visual
---

# Overall description

This R quarto document contains code for figure generation and model interpretation for the relationships between benthic cover and herbivorous fishes abundance (overall and for each feeding group). Additionally, figures for changes in herbivorous fishes and for each feeding group with depth are also included.

# Clean up
```{r}
rm(list=ls())
gc()
```

# =================

# Description

Below this line are R codes for interpreting and plotting the relationships between herbivorous fishes (overall and for each feeding) and benthic categories

# LOAD total herbivore models

```{r}
load("Model_Output/herbs_mod_ab_hab_ver2.Rdata")
load("Model_Output/herbs_food_mod_ver2.Rdata")
```

## Summary tables

# Food model

```{r}
herbs_food_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

# Habitat model

```{r}
herbs_mod_ab_hab |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

# LOAD cropper models

```{r}
load("Model_Output/crop_mod_ab_hab_ver2.Rdata")
load("Model_Output/crop_food_mod_ver2.Rdata")
```

## Summary tables

### Food model

```{r}
crop_food_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

### Habitat model

```{r}
crop_mod_ab_hab |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
         Pg > 0.85)
```

# LOAD detritivore models

```{r}
load("Model_Output/det_mod_hab_ver2.Rdata")
load("Model_Output/det_mod_food_ver2.Rdata")
```

## Summary tables

### Food model

```{r}
det_mod_food |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

### Habitat model

```{r}
det_mod_hab |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

# LOAD scraper models

```{r}
load("Model_Output/scra_hab_mod_ver2.Rdata")
load("Model_Output/scra_food_mod_ver2.Rdata")
```

## Summary table

### Habitat model

```{r}
scra_hab_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

### Food model

```{r}
scra_food_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

# Figure generation

## BENTHIC COMPLEXITY (BC)

### Plot: BC x total herbivore

```{r}
p_thab_bc <-
herbs_mod_ab_hab |> 
  emmeans(~ Benthic_Complexity,
            type = "link") |> 
  #pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  rhat,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  ggplot(aes(x = Benthic_Complexity,
             y = median)) +
  geom_pointrange(aes(ymin = lower,
                      ymax = upper),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "black",
                  fill = "#3C3C3C") +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 20),
  breaks = seq(0, 20, by = 5)) +
  scale_x_discrete(name = "Benthic complexity score") +
  ggtitle("f) Benthic complexity") +
  #(P = 0.89)") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        #axis.ticks = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18)) 
```

### Plot: BC x total herbivore (with images)

```{r}
p_thab_bc <- 
p_thab_bc +
  geom_image(data = tibble(Benthic_Complexity = 1.2,
                           median = 17),
             aes(image = ("Images/BC_Sil.png")),
             size = 0.35) +
  geom_image(data = tibble(Benthic_Complexity = 2.3,
                           median = 19),
             aes(image = ("Images/siganid.png")),
             size = 0.15) +
  geom_image(data = tibble(Benthic_Complexity = 2.3,
                           median = 17),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.15) +
  geom_image(data = tibble(Benthic_Complexity = 2.3,
                           median = 15),
             aes(image = ("Images/scarus.png")),
             size = 0.15)

print(p_thab_bc)
```

#### Pairs: total herbivores

```{r}
herbs_mod_ab_hab |> 
  emmeans(~ Benthic_Complexity,
            type = "link") |> 
  pairs() |> 
  gather_emmeans_draws() |> # odds-ratio
  mutate(.value = exp(.value)) |> # log odds-ratio  
  summarise(median_hdci(.value),
            Pl = mean(.value < 1),
            Pg = mean(.value > 1)) |> 
  filter(Pl > 0.85 | Pg > 0.85)
```

### Plot: BC x cropper

```{r}
p_crop_bc <-
crop_mod_ab_hab |> 
  emmeans(~ Benthic_Complexity,
            type = "link") |> 
  #pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  rhat,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  ggplot(aes(x = Benthic_Complexity,
             y = median)) +
  geom_pointrange(aes(ymin = lower,
                      ymax = upper),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "black",
                  fill = "#3C3C3C") +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 20),
  breaks = seq(0, 20, by = 5)) +
  scale_x_discrete(name = "Benthic complexity score") +
  ggtitle("c) Croppers x Benthic complexity") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18)) 
```

### Plot: BC x cropper (with images)

```{r}
p_crop_bc <-
p_crop_bc +
  geom_image(data = tibble(Benthic_Complexity = 1.2,
                           median = 17),
             aes(image = ("Images/BC_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(Benthic_Complexity = 1.2,
                           median = 12),
             aes(image = ("Images/siganid.png")),
             size = 0.2)

print(p_crop_bc)
```

### Plot: BC x detritivore

No images were attached as no evidence to suggestion relationship between BC and detritivore abundance

```{r}
p_det_bc <-
det_mod_hab |> 
  emmeans(~ Benthic_Complexity,
            type = "link") |> 
  #pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  rhat,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  ggplot(aes(x = Benthic_Complexity,
             y = median)) +
  geom_pointrange(aes(ymin = lower,
                      ymax = upper),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "black",
                  fill = "#3C3C3C") +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 20),
  breaks = seq(0, 20, by = 5)) +
  scale_x_discrete(name = "Score") +
  ggtitle("Detritivores") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18)) 
```

### Plot: BC x scraper

No images were attached as no evidence to suggestion relationship between BC and scraper abundance

```{r}
p_scra_bc <-
scra_hab_mod |> 
  emmeans(~ Benthic_Complexity,
            type = "link") |> 
  #pairs() |> 
  gather_emmeans_draws() |> 
  mutate(Exp = exp(.value)) |> 
  dplyr::select(-.chain, 
                -.value,
                -.iteration) |> 
  summarise_draws(median,
                  HDInterval::hdi,
                  rhat,
                  Pl = ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  ggplot(aes(x = Benthic_Complexity,
             y = median)) +
  geom_pointrange(aes(ymin = lower,
                      ymax = upper),
                  shape = 21,
                  size = 1,
                  fatten = 3,
                  color = "black",
                  fill = "#3C3C3C") +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 20),
  breaks = seq(0, 20, by = 5)) +
  scale_x_discrete(name = "Score") +
  ggtitle("Scrapers") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  annotate("text", 
           x = 4.5, 
           y = 12, 
           label = "Benthic complexity", 
           angle = 90,
           hjust = 0.5)
```

## HARD CORAL

### HC: newdata

```{r}
hc_ab_newdata <- with(fishab_2,
                         data.frame(total_hard_coral = seq(min(total_hard_coral),
                                          max(total_hard_coral),
                                          length = 100)))
```

### Emmeans: HC x total herbivores

```{r}
th_ab_hc <- 
  herbs_mod_ab_hab |> 
  emmeans(~ total_hard_coral,
          at = hc_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

#### Gather emmeans

```{r}
th_ab_hc_draws <- 
gather_emmeans_draws(th_ab_hc)
```

#### Subset 200 draws

```{r}
th_ab_hc_draws_subset <- sample(unique(th_ab_hc_draws$.draw), 200)

th_ab_hc_draws_200 <- th_ab_hc_draws  |>  
  filter(.draw %in% th_ab_hc_draws_subset)
```

#### Plot: HC x total herbivores

```{r}
p_thab_hc <- 
th_ab_hc_draws_200 |> 
  ggplot(aes(x = total_hard_coral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) #+
  #ggtitle("Croppers")
```

### HC x croppers

#### Emmeans: HC x croppers

```{r}
crop_ab_hc <- 
  crop_mod_ab_hab |> 
  emmeans(~ total_hard_coral,
          at = hc_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

#### Gather emmeans

```{r}
crop_ab_hc_draws <- 
gather_emmeans_draws(crop_ab_hc)
```

#### Subset 200 draws

```{r}
crop_ab_hc_draws_subset <- sample(unique(crop_ab_hc_draws$.draw), 200)

cro_ab_hc_draws_200 <- crop_ab_hc_draws  |>  
  filter(.draw %in% crop_ab_hc_draws_subset)
```

#### Plot: HC x croppers

```{r}
p_cropab_hc <- 
cro_ab_hc_draws_200 |> 
  ggplot(aes(x = total_hard_coral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  labs(
    title = "Croppers",        # bigger top title
    subtitle = "Hard coral"     # main plot title
  ) +
  scale_x_continuous(name = "") +
  theme_classic() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 22),
    plot.subtitle = element_text(size = 18)
  )
  
```

### HC x detritivores

#### Emmeans: HC x detritivores

```{r}
det_ab_hc <- 
  det_mod_hab |> 
  emmeans(~ total_hard_coral,
          at = hc_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

#### Gather emmeans

```{r}
det_ab_hc_draws <- 
gather_emmeans_draws(det_ab_hc)
```

#### Subset 200 draws

```{r}
det_ab_hc_draws_subset <- sample(unique(det_ab_hc_draws$.draw), 200)

det_ab_hc_draws_200 <- det_ab_hc_draws  |>  
  filter(.draw %in% det_ab_hc_draws_subset)
```

#### Plot: HC x detritivores 

```{r}
p_detab_hc <- 
det_ab_hc_draws_200 |> 
  ggplot(aes(x = total_hard_coral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        plot.title = element_blank(),
        axis.ticks = element_blank()) #+
  #ggtitle("Croppers")
```

### HC x scrapers

#### Emmeans: HC x scrapers

```{r}
scra_ab_hc <- 
  scra_hab_mod |> 
  emmeans(~ total_hard_coral,
          at = hc_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

#### Gather emmeans

```{r}
scra_ab_hc_draws <- 
gather_emmeans_draws(scra_ab_hc)
```

#### Subset 200 draws

```{r}
scra_ab_hc_draws_subset <- sample(unique(scra_ab_hc_draws$.draw), 200)

scra_ab_hc_draws_200 <- scra_ab_hc_draws  |>  
  filter(.draw %in% scra_ab_hc_draws_subset)
```

#### Plot: HC x scrapers

```{r}
p_scraab_hc <- 
scra_ab_hc_draws_200 |> 
  ggplot(aes(x = total_hard_coral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        plot.title = element_blank(),
        axis.ticks = element_blank()) +
  annotate("text", 
           x = 75, 
           y = 25, 
           label = "Hard coral", 
           angle = 90,
           hjust = 0.5)
  #ggtitle("Croppers")
```

## OCTOCORAL

### OCT: newdata

```{r}
oct_ab_newdata <- with(fishab_2,
                         data.frame(total_octocoral = seq(min(total_octocoral),
                                          max(total_octocoral),
                                          length = 100)))
```

#### OCT x total herbivores

###### Emmeans: OCT x total herbivores

```{r}
th_ab_oct <- 
  herbs_mod_ab_hab |> 
  emmeans(~ total_octocoral,
          at = oct_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

###### Gather emmeans

```{r}
th_ab_oct_draws <- 
gather_emmeans_draws(th_ab_oct)
```

###### Subset 200 draws

```{r}
th_ab_oct_draws_subset <- sample(unique(th_ab_oct_draws$.draw), 200)

th_ab_oct_draws_200 <- th_ab_oct_draws  |>  
  filter(.draw %in% th_ab_oct_draws_subset)
```

###### Plot: OCT x total herbivores

```{r}
p_thab_oct <-
th_ab_oct_draws_200 |> 
  ggplot(aes(x = total_octocoral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFB59E", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorange4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorange4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
theme(axis.title.x = element_blank(),
      axis.text.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))  +
  ggtitle("c) Octocoral")
```

##### Plot: OCT x total herbivores (with images)

```{r}
p_thab_oct <-
p_thab_oct + 
  geom_image(data = tibble(total_octocoral = 5,
                          .value = 43),
             aes(image = ("Images/Octo_Sil.png")),
             size = 0.35) +
  geom_image(data = tibble(total_octocoral = 14,
                           .value = 48),
             aes(image = ("Images/siganid.png")),
             size = 0.15) +
  geom_image(data = tibble(total_octocoral = 14,
                           .value = 43),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.15) +
  geom_image(data = tibble(total_octocoral = 14,
                           .value = 38),
             aes(image = ("Images/scarus.png")),
             size = 0.15)

print(p_thab_oct)
```

##### OCT x croppers

###### Emmeans: OCT x croppers

```{r}
crop_ab_oct <- 
  crop_mod_ab_hab |> 
  emmeans(~ total_octocoral,
          at = oct_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

###### Gather emmeans

```{r}
crop_ab_oct_draws <- 
gather_emmeans_draws(crop_ab_oct)
```

###### Subset 200 draws

```{r}
crop_ab_oct_draws_subset <- sample(unique(crop_ab_oct_draws$.draw), 200)

crop_ab_oct_draws_200 <- crop_ab_oct_draws  |>  
  filter(.draw %in% crop_ab_oct_draws_subset)
```

##### Plot: OCT x croppers

```{r}
p_crop_oct <-
crop_ab_oct_draws_200 |> 
  ggplot(aes(x = total_octocoral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFB59E", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorange4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorange4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme(axis.title.x = element_blank(),
      axis.text.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  ggtitle("a) Croppers x Octocoral")
```

### Plot: OCT x croppers (with images)

```{r}
p_crop_oct <-
p_crop_oct +
  geom_image(data = tibble(total_octocoral = 8,
                           .value = 43),
             aes(image = ("Images/Octo_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(total_octocoral = 8,
                           .value = 30),
             aes(image = ("Images/siganid.png")),
             size = 0.2)

print(p_crop_oct)
```

#### OCT x detritivores

##### Emmeans: OCT x detritivores

```{r}
det_ab_oct <- 
  det_mod_hab |> 
  emmeans(~ total_octocoral,
          at = oct_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
det_ab_oct_draws <- 
gather_emmeans_draws(det_ab_oct)
```

##### Subset 200 draws

```{r}
det_ab_oct_draws_subset <- sample(unique(det_ab_oct_draws$.draw), 200)

det_ab_oct_draws_200 <- det_ab_oct_draws  |>  
  filter(.draw %in% det_ab_oct_draws_subset)
```

##### Plot: OCT x detritivores

```{r}
p_detab_oct <-
det_ab_oct_draws_200 |> 
  ggplot(aes(x = total_octocoral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFB59E", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorange4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorange4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
   theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 15),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 22),
    plot.subtitle = element_text(size = 18)
  ) +
  ggtitle("e) Detritivores x Octocoral")
```

### Plot: OCT x detritivores (with images)

```{r}
p_detab_oct <-
p_detab_oct +
  geom_image(data = tibble(total_octocoral = 8,
                           .value = 43),
             aes(image = ("Images/Octo_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(total_octocoral = 8,
                           .value = 30),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.2)

p_detab_oct
```

#### OCT x scrapers

##### Emmeans: OCT x scrapers

```{r}
scra_ab_oct <- 
  scra_hab_mod |> 
  emmeans(~ total_octocoral,
          at = oct_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
scra_ab_oct_draws <- 
gather_emmeans_draws(scra_ab_oct)
```

##### Subset 200 draws

```{r}
scra_ab_oct_draws_subset <- sample(unique(scra_ab_oct_draws$.draw), 200)

scra_ab_oct_draws_200 <- scra_ab_oct_draws  |>  
  filter(.draw %in% scra_ab_oct_draws_subset)
```

##### Plot: OCT x scrapers

```{r}
p_scraab_oct <-
scra_ab_oct_draws_200 |> 
  ggplot(aes(x = total_octocoral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFB59E", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorange4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorange4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  ggtitle("h) Scrapers x Octocoral") +
  theme(
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 22),
    plot.subtitle = element_text(size = 18)) 
```

##### Plot: OCT x scrapers (with images) 

```{r}
p_scraab_oct <-
p_scraab_oct +
  geom_image(data = tibble(total_octocoral = 8,
                           .value = 43),
             aes(image = ("Images/Octo_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(total_octocoral = 8,
                           .value = 30),
             aes(image = ("Images/scarus.png")),
             size = 0.2)
```

## TURFS

### TA: newdata

```{r}
ta_ab_newdata <- with(fishab_2,
                         data.frame(turf_algae = seq(min(turf_algae),
                                          max(turf_algae),
                                          length = 100)))
```

#### TA x total herbivores

##### Emmeans: TA x total herbivores

```{r}
th_ab_ta <- 
  herbs_food_mod |> 
  emmeans(~ turf_algae,
          at = ta_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
th_ab_ta_draws <- 
gather_emmeans_draws(th_ab_ta)
```

##### Subset 200 draws

```{r}
th_ab_ta_draws_subset <- sample(unique(th_ab_ta_draws$.draw), 200)

th_ab_ta_draws_200 <- th_ab_ta_draws  |>  
  filter(.draw %in% th_ab_ta_draws_subset)
```

##### Plot: TA x total herbivores

```{r}
p_ab_ta <- 
th_ab_ta_draws_200 |> 
  ggplot(aes(x = turf_algae, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#929FBD", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "dodgerblue4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "dodgerblue4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  ggtitle("d) Turfs") +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18))
```

##### Plot: TA x total herbivores (with images)

```{r}
p_ab_ta <-
p_ab_ta + 
  geom_image(data = tibble(turf_algae = 10,
                          .value = 48),
             aes(image = ("Images/Turf_Sil.png")),
             size = 0.35) +
  geom_image(data = tibble(turf_algae = 26,
                           .value = 48),
             aes(image = ("Images/siganid.png")),
             size = 0.15) +
  geom_image(data = tibble(turf_algae = 26,
                           .value = 43),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.15) +
  geom_image(data = tibble(turf_algae = 26,
                           .value = 38),
             aes(image = ("Images/scarus.png")),
             size = 0.15)
```

#### TA x croppers

##### Emmeans: TA x croppers

```{r}
crop_ab_ta <- 
  crop_food_mod |> 
  emmeans(~ turf_algae,
          at = ta_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
crop_ab_ta_draws <- 
gather_emmeans_draws(crop_ab_ta)
```

##### Subset 200 draws

```{r}
crop_ab_ta_draws_subset <- sample(unique(crop_ab_ta_draws$.draw), 200)

crop_ab_ta_draws_200 <- crop_ab_ta_draws  |>  
  filter(.draw %in% crop_ab_ta_draws_subset)
```

##### Plot: TA x croppers

```{r}
p_cropab_ta <- 
crop_ab_ta_draws_200 |> 
  ggplot(aes(x = turf_algae, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#929FBD", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "dodgerblue4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "dodgerblue4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme_classic() +
  ggtitle("b) Croppers x Turfs") +
  theme(
    axis.title = element_blank(),
    axis.text = element_blank(),
    #axis.title.y = element_text(size = 15),
    #axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 22))

```

##### Plot: TA x total croppers (with images)

```{r}
p_cropab_ta <-
p_cropab_ta +
  geom_image(data = tibble(turf_algae = 8,
                          .value = 43),
             aes(image = ("Images/Turf_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(turf_algae = 8,
                           .value = 30),
             aes(image = ("Images/siganid.png")),
             size = 0.2)
```

#### TA x detritivores

##### Emmeans: TA x detritivores

```{r}
det_ab_ta <- 
  det_mod_food |> 
  emmeans(~ turf_algae,
          at = ta_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
det_ab_ta_draws <- 
gather_emmeans_draws(det_ab_ta)
```

##### Subset 200 draws

```{r}
det_ab_ta_draws_subset <- sample(unique(det_ab_ta_draws$.draw), 200)

det_ab_ta_draws_200 <- det_ab_ta_draws  |>  
  filter(.draw %in% det_ab_ta_draws_subset)
```

##### Plot: TA x detritivores

```{r}
p_detab_ta <- 
det_ab_ta_draws_200 |> 
  ggplot(aes(x = turf_algae, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#929FBD", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "dodgerblue4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "dodgerblue4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Cropper~abundance.150m^-2),
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  ggtitle("f) Detritivores x Turfs")+
  scale_x_continuous(name = "") +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        plot.title = element_text(size = 22),
    plot.subtitle = element_text(size = 18)) 

```

##### Plot: TA x detritivores (with images)

```{r}
p_detab_ta <-
p_detab_ta +
  geom_image(data = tibble(turf_algae = 8,
                          .value = 43),
             aes(image = ("Images/Turf_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(turf_algae = 8,
                           .value = 30),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.2)
```

#### TA x scrapers

##### Emmeans: TA x scrapers

```{r}
scra_ab_ta <- 
  scra_food_mod |> 
  emmeans(~ turf_algae,
          at = ta_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
scra_ab_ta_draws <- 
gather_emmeans_draws(scra_ab_ta)
```

##### Subset 200 draws

```{r}
scra_ab_ta_draws_subset <- sample(unique(scra_ab_ta_draws$.draw), 200)

scra_ab_ta_draws_200 <- scra_ab_ta_draws  |>  
  filter(.draw %in% scra_ab_ta_draws_subset)
```

##### Plot: TA x scrapers

```{r}
p_scraab_ta <- 
scra_ab_ta_draws_200 |> 
  ggplot(aes(x = turf_algae, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#929FBD", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "dodgerblue4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "dodgerblue4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  ggtitle("i) Scrapers x Turfs") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 15),
    axis.text.x = element_text(size = 12),
    plot.title = element_text(size = 22))
```

##### Plot: TA x scrapers (with images) 

```{r}
p_scraab_ta <-
p_scraab_ta +
  geom_image(data = tibble(turf_algae = 8,
                          .value = 43),
             aes(image = ("Images/Turf_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(turf_algae = 8,
                           .value = 30),
             aes(image = ("Images/scarus.png")),
             size = 0.2)
```

# MACROALGAE

### MA: newdata

```{r}
ma_ab_newdata <- with(fishab_2,
                         data.frame(total_macroalgae = seq(min(total_macroalgae),
                                          max(total_macroalgae),
                                          length = 100)))
```

#### MA x total herbivores

##### Emmeans: MA x total herbivores

```{r}
th_ab_ma <- 
  herbs_food_mod |> 
  emmeans(~ total_macroalgae,
          at = ma_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
th_ab_ma_draws <- 
gather_emmeans_draws(th_ab_ma)
```

##### Subset 200 draws

```{r}
th_ab_ma_draws_subset <- sample(unique(th_ab_ma_draws$.draw), 200)

th_ab_ma_draws_200 <- th_ab_ma_draws  |>  
  filter(.draw %in% th_ab_ma_draws_subset)
```

##### Plot: MA x total herbivores

```{r}
p_th_ab_ma <- 
th_ab_ma_draws_200 |> 
  ggplot(aes(x = total_macroalgae, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#8AA17D", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkgreen", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkgreen", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  ggtitle("e) Macroalgae") +
  theme(
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18)) 
```

##### Plot: MA x total herbivores (with images)

```{r}
p_th_ab_ma <-
p_th_ab_ma + 
  geom_image(data = tibble(total_macroalgae = 10,
                          .value = 40),
             aes(image = ("Images/MA_Sil.png")),
             size = 0.35) +
  geom_image(data = tibble(total_macroalgae = 26,
                           .value = 48),
             aes(image = ("Images/siganid.png")),
             size = 0.15) +
  geom_image(data = tibble(total_macroalgae = 26,
                           .value = 43),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.15) +
  geom_image(data = tibble(total_macroalgae = 26,
                           .value = 38),
             aes(image = ("Images/scarus.png")),
             size = 0.15)

print(p_th_ab_ma)
```

##### MA: croppers

##### emmeans: MA x croppers

```{r}
crop_ab_ma <- 
  crop_food_mod |> 
  emmeans(~ total_macroalgae,
          at = ma_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
crop_ab_ma_draws <- 
gather_emmeans_draws(crop_ab_ma)
```

##### Subset 200 draws

```{r}
crop_ab_ma_draws_subset <- sample(unique(crop_ab_ma_draws$.draw), 200)

crop_ab_ma_draws_200 <- crop_ab_ma_draws  |>  
  filter(.draw %in% crop_ab_ma_draws_subset)
```

##### Plot: MA x croppers

```{r}
p_crop_ab_ma <- 
crop_ab_ma_draws_200 |> 
  ggplot(aes(x = total_macroalgae, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#8AA17D", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkgreen", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkgreen", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme_classic() +
  ggtitle("d) Croppers x Macroalgae") +
  theme(axis.title = element_blank(),
        axis.text = element_blank()) 

print(p_crop_ab_ma)
```

##### Plot: MA x croppers (with images)

```{r}
p_crop_ab_ma <-
p_crop_ab_ma + 
  geom_image(data = tibble(total_macroalgae = 8,
                          .value = 43),
             aes(image = ("Images/MA_Sil.png")),
             size = 0.2) + 
  geom_image(data = tibble(total_macroalgae = 8,
                           .value = 30),
             aes(image = ("Images/siganid.png")),
             size = 0.2)
```

##### MA: detritivores

##### Emmeans: MA x detritivores

```{r}
det_ab_ma <- 
  det_mod_food |> 
  emmeans(~ total_macroalgae,
          at = ma_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
det_ab_ma_draws <- 
gather_emmeans_draws(det_ab_ma)
```

##### Subset 200 draws

```{r}
det_ab_ma_draws_subset <- sample(unique(det_ab_ma_draws$.draw), 200)

det_ab_ma_draws_200 <- det_ab_ma_draws  |>  
  filter(.draw %in% det_ab_ma_draws_subset)
```

##### Plot: MA x detritivores

```{r}
p_det_ab_ma <- 
det_ab_ma_draws_200 |> 
  ggplot(aes(x = det_ab_ma_draws_200, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#8AA17D", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkgreen", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkgreen", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,60),
                     breaks = seq(0, 60, by = 20)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme_classic() +
  #ggtitle("P = 0.95") +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_blank()) 
```

##### MA: scrapers

##### Emmeans: MA x scrapers

```{r}
scra_ab_ma <- 
  scra_food_mod |> 
  emmeans(~ total_macroalgae,
          at = ma_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
scra_ab_ma_draws <- 
gather_emmeans_draws(scra_ab_ma)
```

##### Subset 200 draws

```{r}
scra_ab_ma_draws_subset <- sample(unique(scra_ab_ma_draws$.draw), 200)

scra_ab_ma_draws_200 <- scra_ab_ma_draws  |>  
  filter(.draw %in% scra_ab_ma_draws_subset)
```

##### Plot: MA x scrapers

```{r}
p_scraab_ma <- 
scra_ab_ma_draws_200 |> 
  ggplot(aes(x = total_macroalgae, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#8AA17D", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkgreen", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkgreen", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  ggtitle("k) Scrapers x Macroalgae") +
 theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 22),
    plot.subtitle = element_text(size = 18)) 
```

##### Plot: MA x scrapers (with images)

```{r}
p_scraab_ma <-
p_scraab_ma + 
  geom_image(data = tibble(total_macroalgae = 8,
                          .value = 43),
             aes(image = ("Images/MA_Sil.png")),
             size = 0.2) + 
  geom_image(data = tibble(total_macroalgae = 8,
                           .value = 30),
             aes(image = ("Images/scarus.png")),
             size = 0.2)

p_scraab_ma
```

# SPONGE

## SP: newdata

```{r}
sp_ab_newdata <- with(fishab_2,
                         data.frame(sponge = seq(min(sponge),
                                          max(sponge),
                                          length = 100)))
```

#### SP x total herbivores

##### Emmeans: SP x total herbivores

```{r}
th_ab_sp <- 
  herbs_food_mod |> 
  emmeans(~ sponge,
          at = sp_ab_newdata,
          data = fishab_2,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
th_ab_sp_draws <- 
gather_emmeans_draws(th_ab_sp)
```

##### Subset 200 draws

```{r}
th_ab_sp_draws_subset <- sample(unique(th_ab_sp_draws$.draw), 200)

th_ab_sp_draws_200 <- th_ab_sp_draws  |>  
  filter(.draw %in% th_ab_sp_draws_subset)
```

##### Plot: SP x total herbivores

```{r}
p_thab_sp <- 
th_ab_sp_draws_200 |> 
  ggplot(aes(x = sponge, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#E29297", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "firebrick4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "firebrick4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  ggtitle("Sponge") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) 
```

#### SP: croppers

##### Emmeans: SP x croppers 

```{r}
crop_ab_sp <- 
  crop_food_mod |> 
  emmeans(~ sponge,
          at = sp_ab_newdata,
          data = fishab_2,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
crop_ab_sp_draws <- 
gather_emmeans_draws(crop_ab_sp)
```

##### Subset 200 draws

```{r}
crop_ab_sp_draws_subset <- sample(unique(crop_ab_sp_draws$.draw), 200)

crop_ab_sp_draws_200 <- crop_ab_sp_draws  |>  
  filter(.draw %in% crop_ab_sp_draws_subset)
```

##### Plot: SP x croppers 

```{r}
p_cropab_sp <- 
crop_ab_sp_draws_200 |> 
  ggplot(aes(x = sponge, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#E29297", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "firebrick4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "firebrick4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  #ggtitle("P = 0.91") +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_blank())
```

#### SP: detritivores

##### Emmeans: SP x detritivores

```{r}
det_ab_sp <- 
  det_mod_food |> 
  emmeans(~ sponge,
          at = sp_ab_newdata,
          data = fishab_2,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
det_ab_sp_draws <- 
gather_emmeans_draws(det_ab_sp)
```

##### Subset 200 draws

```{r}
det_ab_sp_draws_subset <- sample(unique(det_ab_sp_draws$.draw), 200)

det_ab_sp_draws_200 <- det_ab_sp_draws  |>  
  filter(.draw %in% det_ab_sp_draws_subset) |> 
  filter(.value < 200)
```

##### Plot: SP x detritivores

```{r}
p_detab_sp <- 
det_ab_sp_draws_200 |> 
  ggplot(aes(x = sponge, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#E29297", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "firebrick4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "firebrick4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  ggtitle("g) Detritivores x Sponge") +
    theme(axis.title = element_blank(),
        axis.text = element_blank(),
       #axis.ticks = element_blank(),
       plot.title = element_text(size = 22),
    plot.subtitle = element_text(size = 18)
)   
```

### Plot: SP x detritivores (with images)

```{r}
p_detab_sp <-
p_detab_sp +
  geom_image(data = tibble(sponge = 5,
                          .value = 43),
             aes(image = ("Images/Sponge_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(sponge = 5,
                           .value = 30),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.2)

p_detab_sp
```

#### SP x scrapers

##### Emmeans: SP x scrapers

```{r}
scra_ab_sp <- 
  scra_food_mod  |> 
  emmeans(~ sponge,
          at = sp_ab_newdata,
          type = "response",
          epred = "TRUE") 
```

##### Gather emmeans

```{r}
scra_ab_sp_draws <- 
gather_emmeans_draws(scra_ab_sp)
```

##### Subset 200 draws

```{r}
scra_ab_sp_draws_subset <- sample(unique(scra_ab_sp_draws$.draw), 200)

scra_ab_sp_draws_200 <- scra_ab_sp_draws  |>  
  filter(.draw %in% scra_ab_sp_draws_subset) |> 
  filter(max(.value) <= 5) |>
  ungroup()
```

##### Plot: SP x scrapers

```{r}
p_scraab_sp <- 
scra_ab_sp_draws_200 |> 
  ggplot(aes(x = sponge, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#E29297", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "firebrick4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "firebrick4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                    limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  ggtitle("j) Scrapers x Sponge") +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 22)) 
```

### Plot: SP x scrapers (with images)

```{r}
p_scraab_sp <-
p_scraab_sp +
  geom_image(data = tibble(sponge = 1.5,
                          .value = 43),
             aes(image = ("Images/Sponge_Sil.png")),
             size = 0.2) +
  geom_image(data = tibble(sponge = 1.5,
                           .value = 30),
             aes(image = ("Images/scarus.png")),
             size = 0.2)

p_scraab_sp
```

# Combine plots: benthic categories x abundance

```{r}
p_fg_ab <-
wrap_plots(
  p_crop_oct,   p_cropab_ta, p_crop_bc,   p_crop_ab_ma,
  p_detab_oct,  p_detab_ta,  p_detab_sp,  plot_spacer(),
  p_scraab_oct, p_scraab_ta, p_scraab_sp, p_scraab_ma,
  ncol = 4
) &
  theme(
    plot.title = element_text(size = 18, hjust = 0)
  )
```

# ggsave

```{r}
ggsave("Figures/p_fg_ab_ver2.jpeg",
       plot =p_fg_ab, 
       dpi = 600, 
       height = 15, 
       width = 17, 
       units = "in")
```

# =========================

# Description

Below this line are code for the interpretation and figure generation of changes in herbivore abundance (total and for each feeding group) with depth

# ABUNDANCE SUMMARY TABLE

## Summary table: depth x abun total herbs

```{r}
herbs_depthmod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

## Summary table: depth x abun crops

```{r}
crops_depthmod|> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

## Summary table: depth x abun det

```{r}
det_depthmod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

## Summary table: depth x abun scra

```{r}
scra_depthmod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

# Plotting

# TOTAL HERBS

## Load model

```{r}
load("Model_Output/herbs_depthmod_ab.Rdata")
```

## Newdata

```{r}
depthabun_newdata <- with(fishab_2,
                      data.frame(Depth_m = seq(min(Depth_m),
                                             max(Depth_m),
                                             length = 100)))
```

## Emmeans

```{r}
fishabun_em <- 
  herbs_depthmod |> 
  emmeans(~ Depth_m,
          at = depthabun_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
fishabun_em_draws <- 
gather_emmeans_draws(fishabun_em)
```

## Subset 200 draws

```{r}
fishabun_draw_subset <- sample(unique(fishabun_em_draws$.draw), 200)

fishabun_em_draws_200 <- fishabun_em_draws  |>  
  filter(.draw %in% fishabun_draw_subset)

```

## Plot

```{r}
p2_depth_th <- 
fishabun_em_draws_200 |> 
  ggplot(aes(x = Depth_m, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#929FBD", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "dodgerblue4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "dodgerblue4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                     limits = c(0,80),
                     breaks = seq(0, 80, by = 20)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  ggtitle("Total herbivores") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# CROPPERS

## Load model

```{r}
load("Model_Output/crops_depthmod_ab.Rdata")
```

## Newdata

```{r}
depthabun_newdata <- with(fishab_2,
                      data.frame(Depth_m = seq(min(Depth_m),
                                             max(Depth_m),
                                             length = 100)))
```

## Emmeans

```{r}
cropabun_em <- 
 crops_depthmod |> 
  emmeans(~ Depth_m,
          at = depthabun_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
cropabun_em_draws <- 
gather_emmeans_draws(cropabun_em)
```

## Subset 200 draws

```{r}
cropabun_draw_subset <- sample(unique(cropabun_em_draws$.draw), 200)

cropabun_em_draws_200 <- cropabun_em_draws  |>  
  filter(.draw %in% cropabun_draw_subset)
```

## Plot

```{r}
p3_depth_crop <- 
cropabun_em_draws_200 |> 
  ggplot(aes(x = Depth_m, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                     limits = c(0,80),
                     breaks = seq(0, 80, by = 20)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  ggtitle("Cropper") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18))
```

# DETRITIVORE

## Load model

```{r}
load("Model_Output/det_depthmod_ab.Rdata")
```

## Newdata

```{r}
depthabun_newdata <- with(fishab_2,
                      data.frame(Depth_m = seq(min(Depth_m),
                                             max(Depth_m),
                                             length = 100)))
```

## Emmeans

```{r}
detabun_em <- 
 det_depthmod |> 
  emmeans(~ Depth_m,
          at = depthabun_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
detabun_em_draws <- 
gather_emmeans_draws(detabun_em)
```

## Subset 200 draws

```{r}
detabun_draw_subset <- sample(unique(detabun_em_draws$.draw), 200)

detabun_em_draws_200 <- detabun_em_draws  |>  
  filter(.draw %in% detabun_draw_subset)
```

## Plot

```{r}
p4_depth_det <- 
detabun_em_draws_200 |> 
  ggplot(aes(x = Depth_m, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFB59E", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorange4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorange4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                     limits = c(0,80),
                     breaks = seq(0, 80, by = 20)) +
  theme_classic() +
  scale_x_continuous(name = "Depth (m)") +
  ggtitle("Detritivore") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# SCRAPER

## Load model

```{r}
load("Model_Output/scra_depthmod_ab.Rdata")
```

## Newdata

```{r}
depthabun_newdata <- with(fishab_2,
                      data.frame(Depth_m = seq(min(Depth_m),
                                             max(Depth_m),
                                             length = 100)))
```

## Emmeans

```{r}
scraabun_em <- 
 scra_depthmod |> 
  emmeans(~ Depth_m,
          at = depthabun_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
scraabun_em_draws <- 
gather_emmeans_draws(scraabun_em)
```

## Subset 200 draws

```{r}
scraabun_draw_subset <- sample(unique(scraabun_em_draws$.draw), 200)

scraabun_em_draws_200 <- scraabun_em_draws  |>  
  filter(.draw %in% scraabun_draw_subset)
```

## Plot

```{r}
p5_depth_scra <- 
scraabun_em_draws_200 |> 
  ggplot(aes(x = Depth_m, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFAECF", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorchid4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorchid4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                     limits = c(0,80),
                     breaks = seq(0, 80, by = 20)) +
  theme_classic() +
  scale_x_continuous(name = "Depth (m)") +
  ggtitle("Scraper") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18))
```

# Combine plots

```{r}
p_depth_sp_ab <-
(p1_depth_spr + plot_spacer()) /
  (p2_depth_th + p3_depth_crop) /
  (p4_depth_det + p5_depth_scra)  +
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

# ggsave

```{r}
ggsave("Figures/p_depth_sp_ab.jpeg",
       plot = p_depth_sp_ab, 
       dpi = 600, 
       height = 11, 
       width = 9, 
       units = "in")
```