---
title: "Untitled"
format: html
editor: visual
---

# Description

This qmd file contains code for the generation of figures and interpretation of models

# Cleanup

```{r}
rm(list=ls())
gc()
```

# Load custom functions

```{r}
source("helperFunctions.R")
```

# Load models

```{r}
load("Model_Outputs/herbs_sp_hab_mod.Rdata")
load("Model_Outputs/herbs_sp_food_mod.Rdata")
```

## Summary table: habitat x species richness

```{r}
herbs_sp_hab_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

## Summary table: food x species richness

```{r}
herbs_sp_food_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

# Figures

# HARD CORAL

### New data: hard coral

```{r}
hc_sp_newdata <- with(sprich_v2,
                         data.frame(total_hard_coral = seq(min(total_hard_coral),
                                          max(total_hard_coral),
                                          length = 100)))
```

## Emmeans

```{r}
sp_hc_em <- 
  herbs_sp_hab_mod |> 
  emmeans(~ total_hard_coral,
          at = hc_sp_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
sp_hc_em_draws <- 
gather_emmeans_draws(sp_hc_em)
```

## Subset 200 draws

```{r}
sp_hc_draw_subset <- sample(unique(sp_hc_em_draws$.draw), 200)

sp_hc_em_draws_200 <- sp_hc_em_draws  |>  
  filter(.draw %in% sp_hc_draw_subset)
```

## Plot: hard coral

```{r}
p_sp_hc <-
sp_hc_em_draws_200 |> 
  ggplot(aes(x = total_hard_coral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Richness~(species.150m^-2)),
                       limits = c(0, 40),
  breaks = seq(0, 40, by = 10)) +
  scale_x_continuous(name = "",
                     breaks = seq(0, 100, by = 25)) +
  theme_classic() +
  ggtitle("b) Hard coral") +
  scale_x_continuous(name = "Hard coral cover (%)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks = element_blank(),
        axis.title.y =  element_blank(),
        axis.text.y =  element_blank(),
        plot.title = element_text(size = 18))
```

## Plot: hard coral (with images)

```{r}
p_sp_hc <-
p_sp_hc + 
  geom_image(data = tibble(total_hard_coral = 10,
                          .value = 35),
             aes(image = ("Images/HC_Sil.png")),
             size = 0.35) +
  geom_image(data = tibble(total_hard_coral = 25,
                           .value = 38),
             aes(image = ("Images/siganid.png")),
             size = 0.15) +
  geom_image(data = tibble(total_hard_coral = 25,
                           .value = 34),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.15) +
  geom_image(data = tibble(total_hard_coral = 25,
                           .value = 30),
             aes(image = ("Images/scarus.png")),
             size = 0.15)
```

### OCTOCORAL

## Newdata: Octocoral

```{r}
oct_sp_newdata <- with(sprich_v2,
                         data.frame(total_octocoral = seq(min(total_octocoral),
                                          max(total_octocoral),
                                          length = 100)))
```

## Emmeans

```{r}
sp_oct_em <- 
  herbs_sp_hab_mod |> 
  emmeans(~ total_octocoral,
          at = oct_sp_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
sp_oct_em_draws <- 
gather_emmeans_draws(sp_oct_em)
```

## Subset 200 draws

```{r}
sp_oct_draw_subset <- sample(unique(sp_oct_em_draws$.draw), 200)

sp_oct_em_draws_200 <- sp_oct_em_draws  |>  
  filter(.draw %in% sp_oct_draw_subset)
```

## Plot: Octocoral

```{r}
p_sp_oct <-
sp_oct_em_draws_200 |> 
  ggplot(aes(x = total_octocoral, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFB59E", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorange4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorange4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Richness~(species.150m^-2)),
                       limits = c(0, 40),
  breaks = seq(0, 40, by = 10)) +
  scale_x_continuous(name = "",
                     breaks = seq(0, 40, by = 10)) +
  theme_classic() +
  ggtitle("a) Octocoral") +
  #scale_x_continuous(name = "Octocoral cover (%)") +
  theme(axis.title.x = element_blank(),
        axis.text.x =element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))  #+
  #ggtitle("Species richness")
```

## Plot: Octocoral (with images)

```{r}
p_sp_oct <-
p_sp_oct + 
  geom_image(data = tibble(total_octocoral = 5,
                          .value = 33),
             aes(image = ("Images/Octo_Sil.png")),
             size = 0.35) +
  geom_image(data = tibble(total_octocoral = 12,
                           .value = 38),
             aes(image = ("Images/siganid.png")),
             size = 0.15) +
  geom_image(data = tibble(total_octocoral = 12,
                           .value = 34),
             aes(image = ("Images/ctenochaetus.png")),
             size = 0.15) +
  geom_image(data = tibble(total_octocoral = 12,
                           .value = 30),
             aes(image = ("Images/scarus.png")),
             size = 0.15)

print(p_sp_oct)
```

# COMBINE FIGS

```{r}
p_total_sp_ab <- 
(p_sp_oct + p_sp_hc) /
  (p_thab_oct + p_ab_ta) /
  (p_th_ab_ma + p_thab_bc) +
  theme(
    plot.title = element_text(size = 15, hjust = 0)
  )
```

# ggsave

```{r}
ggsave("Figures/p_total_sp_ab_ver2.jpeg",
       plot =p_total_sp_ab, 
       dpi = 600, 
       height = 11, 
       width = 9, 
       units = "in")
```

# ==================

# Description

Below this line are R code that generated figures and interpreted model outputs for species richness and how this changes with depth

# Load model

```{r}
load("Model_Outputs/herbs_fishspecies_depth_mod.Rdata")
```

## Summary table: depth

```{r}
herbs_fishsp_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

## Newdata: species richness

```{r}
depthsp_newdata <- with(sprich_v2,
                      data.frame(Depth = seq(min(Depth),
                                             max(Depth),
                                             length = 100)))
```

## Emmeans

```{r}
fishsp_em <- 
  herbs_fishsp_mod |> 
  emmeans(~ Depth,
          at = depthsp_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
fish_em_draws <- 
gather_emmeans_draws(fishsp_em)
```

## Subset 200 draws

```{r}
fishsp_draw_subset <- sample(unique(fish_em_draws$.draw), 200)

fishsp_em_draws_200 <- fish_em_draws  |>  
  filter(.draw %in% fishsp_draw_subset)
```

## Plot: depth

```{r}
p1_depth_spr <- 
fishsp_em_draws_200 |> 
  ggplot(aes(x = Depth, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#8AA17D", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkgreen", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkgreen", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Richness~(species.150m^-2)),
                     limits = c(0,30),
                     breaks = seq(0, 30, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  ggtitle("Herbivore richness") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```
