---
title: "BC_Fish_Spr_Fits"
format: html
editor: visual
---

# Overall description

This qmd file contains R code for the model fitting and validation of the relationship between species richness of herbivorous fishes and benthic categories

# Clean up

```{r}
rm(list=ls())
gc()
```

# Library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(car)
library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# Load csv

```{r}
sprich <- read_csv("Data/relationship_fish_sp_ben_v2.csv",
                           trim_ws = TRUE)
```

# Isolate important variables

```{r}
sprich_v2 <- 
  sprich |> 
  mutate(total_octocoral = complex_octocoral + other_octocoral) |> 
  select(Depth,
         Habitat,
         #Aspect_descriptive,
         Site_recode,
         Estimator,
         turf_algae,
         sponge,
         unconsolidated_subs,
         total_macroalgae,
         total_hard_coral,
         total_octocoral,
         median_complexity) |> 
  mutate(median_complexity = factor(median_complexity)) |> 
  filter(Habitat == "outer_reef")
```

# Exploratory data analysis

```{r}
sprich_v2 |> 
  ggplot(aes(x = turf_algae, y = Estimator)) +
  geom_point()

sprich_v2 |> 
  ggplot(aes(x = macroalgae, y = Estimator)) +
  geom_point()

sprich_v2 |> 
  ggplot(aes(x = total_hard_coral, y = Estimator)) +
  geom_point()
```

# Description

Below this line are codes to examine the relationship between species richness of herbivorous fishes and benthic categories

# TOTAL HERBIVORES

# HABITAT MODEL

## Def formula

```{r}
herbs_form_sp_hab <- bf(Estimator ~ 
                  #turf_algae +
                   #sponge +
                     unconsolidated_subs +
                     #total_macroalgae +
                     total_hard_coral +
                     total_octocoral +
                     median_complexity +
                   (1 | Site_recode), #+
                     #(1 | Habitat_type) +
                     #(1 | Aspect_descriptive),
                 family = lognormal())
```

## Weakly informed priors

```{r}
herb_sp_priors <- prior(normal(1.1, 1.2), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(student_t(3, 0, 1.2), class = "sigma") +
  prior(student_t(3, 0, 1.2), class = "sd") # +
  #prior(beta(1, 1), class = "hu")
```

## Prior only model

```{r}
#| cache: true
herbs_sp_prior_hab_mod <- brm(herbs_form_sp_hab,
                    data = sprich_v2,
                    prior = herb_sp_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 2000)
```

## Fit the model

```{r}
#| cache: true
herbs_sp_hab_mod <- update(herbs_sp_prior_hab_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    save_pars = save_pars(all = TRUE), # required for loo_comparison
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
herbs_sp_hab_mod|> mcmc_plot(type = "trace")
# autocorr
herbs_sp_hab_mod |> mcmc_plot(type = "acf_bar")

# rhat
herbs_sp_hab_mod|> mcmc_plot(type = "rhat_hist")

# ess
herbs_sp_hab_mod |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
herbs_sp_hab_resids <- make_brms_dharma_res(herbs_sp_hab_mod)

# qqplot
herbs_sp_hab_resids |> testUniformity()

# residplot
herbs_sp_hab_resids |> plotResiduals(quantreg = FALSE)

# testdisp
herbs_sp_hab_resids |> testDispersion()
```

# Save model

```{r}
save(herbs_sp_hab_mod, file = "Model_Outputs/herbs_sp_hab_mod_ver2.Rdata")
```

# FOOD MODEL

## Def formula

```{r}
herbs_form_sp_food <- bf(Estimator ~ 
                  turf_algae +
                   sponge +
                    # unconsolidated_subs +
                     total_macroalgae +
                     #total_hard_coral +
                     #total_octocoral +
                     #median_complexity +
                   (1 | Site_recode),# +
                     #(1 | Habitat_type) +
                     #(1 | Aspect_descriptive),
                 family = lognormal())
```

## Prior only model

```{r}
#| cache: true
herbs_sp_prior_food_mod <- brm(herbs_form_sp_food,
                    data = sprich_v2,
                    prior = herb_sp_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 2000)
```

## Fit the model

```{r}
#| cache: true
herbs_sp_food_mod <- update(herbs_sp_prior_food_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    save_pars = save_pars(all = TRUE), # required for loo_comparison
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
herbs_sp_food_mod|> mcmc_plot(type = "trace")
# autocorr
herbs_sp_food_mod |> mcmc_plot(type = "acf_bar")

# rhat
herbs_sp_food_mod|> mcmc_plot(type = "rhat_hist")

# ess
herbs_sp_food_mod |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
herbs_sp_food_resids <- make_brms_dharma_res(herbs_sp_food_mod)

# qqplot
herbs_sp_food_resids |> testUniformity()

# residplot
herbs_sp_food_resids |> plotResiduals(quantreg = FALSE)

# testdisp
herbs_sp_food_resids |> testDispersion()
```

# Save model

```{r}
save(herbs_sp_food_mod, file = "Model_Outputs/herbs_sp_food_mod_ver2.Rdata")
```

# ==========================

# Description

Below this line are code for modelling and validating changes in species richness with depth

## Def formula

```{r}
herbs_form_fishsp <- bf(Estimator ~ 
                  Depth  +
                   (1 | Site_recode), #+
                     #(1 | Habitat_type) +
                     #(1 | Aspect_descriptive),
                 family = lognormal())
```

## Weakly informed priors

```{r}
herb_fishsp_priors <- prior(normal(1.1, 1.2), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(student_t(3, 0, 1.2), class = "sigma") +
  prior(student_t(3, 0, 1.2), class = "sd")
```

## Prior only model

```{r}
#| cache: true
herbs_fishsp_prior_mod <- brm(herbs_form_fishsp,
                    data = sprich_v2,
                    prior = herb_fishsp_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 2000)
```

## Fit the model

```{r}
#| cache: true
herbs_fishsp_mod <- update(herbs_fishsp_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    save_pars = save_pars(all = TRUE), # required for loo_comparison
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
herbs_fishsp_mod|> mcmc_plot(type = "trace")
# autocorr
herbs_fishsp_mod |> mcmc_plot(type = "acf_bar")

# rhat
herbs_fishsp_mod|> mcmc_plot(type = "rhat_hist")

# ess
herbs_fishsp_mod |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
herbs_fishsp_resids <- make_brms_dharma_res(herbs_fishsp_mod)

# qqplot
herbs_fishsp_resids |> testUniformity()

# residplot
herbs_fishsp_resids |> plotResiduals(quantreg = FALSE)

# testdisp
herbs_fishsp_resids |> testDispersion()
```

# Save model

```{r}
save(herbs_fishsp_mod, file = "Model_Outputs/herbs_fishspecies_depth_mod_ver2.Rdata")
```
