---
title: "benthic_model_fits_glmms"
format: html
editor: visual
---

# CORAL

## def formula

```{r}
coral_form_glm <- bf(prop_hc ~ Depth +
                   (1 | Site_recode),
                 family = zero_inflated_beta())
```

## get prio

```{r}
get_prior(coral_form_glm, data = benthic_v2)
```

## def prior

```{r}
coral_prior_glm <- prior(normal(2.2, 1.7), class = "Intercept") +
  prior(normal(0, 1.3), class = "b") +
  #prior(student_t(3, 0 , 1.7), class = "sds") +
  prior(student_t(3, 0, 1.7), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## fit full model

```{r}
#| cache: TRUE
coral_mod_glm <- brm(coral_form_glm,
                data = benthic_v2,
                prior = coral_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 0)
```

### MCMC diagnostics

```{r}
coral_mod_glm |> mcmc_plot(type = "trace")
coral_mod_glm |> mcmc_plot(type = "acf_bar")
coral_mod_glm |> mcmc_plot(type = "rhat_hist")
coral_mod_glm |> mcmc_plot(type = "neff_hist")
```

### residuals

```{r}
coral_resids_glm <- make_brms_dharma_res(coral_mod_glm)

# qqplot
coral_resids_glm |> testUniformity()
coral_resids_glm |> plotResiduals(quantreg = FALSE)
```

# MACROALGAE

## def formula

```{r}
ma_form_glm <- bf(prop_ma ~ Depth +
                   (1 | Site_recode),
                 family = zero_inflated_beta())
```

## def prior

```{r}
ma_prior_glm <- prior(normal(1.8, 1.4), class = "Intercept") +
  prior(normal(0, 1.3), class = "b") +
  #prior(student_t(3, 0 , 1.4), class = "sds") +
  prior(student_t(3, 0, 1.4), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## fit full model

```{r}
#| cache: TRUE
ma_mod_glm <- brm(ma_form_glm,
                data = benthic_v2,
                prior = ma_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 0)
```

### MCMC diagnostics

```{r}
ma_mod_glm |> mcmc_plot(type = "trace")
ma_mod_glm |> mcmc_plot(type = "acf_bar")
ma_mod_glm |> mcmc_plot(type = "rhat_hist")
ma_mod_glm |> mcmc_plot(type = "neff_hist")
```

### residuals

```{r}
ma_resids_glm <- make_brms_dharma_res(ma_mod_glm)

# qqplot
ma_resids_glm |> testUniformity()
ma_resids_glm |> plotResiduals(quantreg = FALSE)
```

- residuals could be better

# TURF ALGAE

## def formula

```{r}
ta_form_glm <- bf(prop_ta ~ Depth +
                   (1 | Site_recode),
                 family = zero_inflated_beta())
```

## def prior

```{r}
ta_prior_glm <- prior(normal(2.6, 2.2), class = "Intercept") +
  prior(normal(0, 1.2), class = "b") +
  #prior(student_t(3, 0 , 2.2), class = "sds") +
  prior(student_t(3, 0, 2.2), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## fit full model

```{r}
#| cache: TRUE
ta_mod_glm <- brm(ta_form_glm,
                data = benthic_v2,
                prior = ta_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 0)
```

### MCMC diagnostics

```{r}
ta_mod_glm |> mcmc_plot(type = "trace")
ta_mod_glm |> mcmc_plot(type = "acf_bar")
ta_mod_glm |> mcmc_plot(type = "rhat_hist")
ta_mod_glm |> mcmc_plot(type = "neff_hist")
```

### residuals

```{r}
ta_resids_glm <- make_brms_dharma_res(ta_mod_glm)

# qqplot
ta_resids_glm |> testUniformity()
ta_resids_glm |> plotResiduals(quantreg = FALSE)
```

# OCTOCORAL

## def formula

```{r}
oct_form_glm <- bf(prop_oct ~ Depth +
                   (1 | Site_recode),
                 family = zero_inflated_beta())
```

## def prior

```{r}
oct_prior_glm <- prior(normal(2.5, 2), class = "Intercept") +
  prior(normal(0, 1.2), class = "b") +
  #prior(student_t(3, 0 , 2), class = "sds") +
  prior(student_t(3, 0, 2), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## fit full model

```{r}
#| cache: TRUE
oct_mod_glm <- brm(oct_form_glm,
                data = benthic_v2,
                prior = oct_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 0)
```

### MCMC diagnostics

```{r}
oct_mod_glm |> mcmc_plot(type = "trace")
oct_mod_glm |> mcmc_plot(type = "acf_bar")
oct_mod_glm |> mcmc_plot(type = "rhat_hist")
oct_mod_glm |> mcmc_plot(type = "neff_hist")
```

### residuals

```{r}
oct_resids_glm <- make_brms_dharma_res(oct_mod_glm)

oct_resids_glm |> testUniformity()
oct_resids_glm |> plotResiduals(quantreg = FALSE)
```

- residuals could be better

# ROCK

rock

## def formula

```{r}
rock_form_glm <- bf(prop_rock ~ Depth +
                   (1 | Site_recode),
                 family = zero_inflated_beta())
```

## def prior

```{r}
rock_prior_glm <- prior(normal(3, 2.5), class = "Intercept") +
  prior(normal(0, 1.2), class = "b") +
  #prior(student_t(3, 0 , 2.5), class = "sds") +
  prior(student_t(3, 0, 2.5), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## fit full model

```{r}
#| cache: TRUE
rock_mod_glm <- brm(rock_form_glm,
                data = benthic_v2,
                prior = rock_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 0)
```

### MCMC diagnostics

```{r}
rock_mod_glm |> mcmc_plot(type = "trace")
rock_mod_glm |> mcmc_plot(type = "acf_bar")
rock_mod_glm |> mcmc_plot(type = "rhat_hist")
rock_mod_glm |> mcmc_plot(type = "neff_hist")
```

### residuals

```{r}
rock_resids_glm <- make_brms_dharma_res(rock_mod_glm)

rock_resids_glm |> testUniformity()
rock_resids_glm |> plotResiduals(quantreg = FALSE)
```

# UNCONSOLIDATED SUBSTRATE

## def formula

```{r}
us_form_glm <- bf(prop_us ~ Depth +
                   (1 | Site_recode),
                 family = zero_one_inflated_beta())
```

## def prior

```{r}
us_prior_glm <- prior(normal(1.9, 1.4), class = "Intercept") +
  prior(normal(0, 1.3), class = "b") +
  #prior(student_t(3, 0 , 1.4), class = "sds") +
  prior(student_t(3, 0, 1.4), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1, 1), class = "coi") +
  prior(beta(1, 1), class = "zoi")
```

## fit full model

```{r}
#| cache: TRUE
us_mod_glm <- brm(us_form_glm,
                data = benthic_v2,
                prior = us_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 0)
```

### MCMC diagnostics

```{r}
us_mod_glm |> mcmc_plot(type = "trace")
us_mod_glm |> mcmc_plot(type = "acf_bar")
us_mod_glm |> mcmc_plot(type = "rhat_hist")
us_mod_glm |> mcmc_plot(type = "neff_hist")
```

### residuals

```{r}
us_resids_glm <- make_brms_dharma_res(us_mod_glm)

us_resids_glm |> testUniformity()
us_resids_glm |> plotResiduals(quantreg = FALSE)
```

# LOO COMPARE

- understanding loo compare:
  - greater loo (elpd diff) is the best model
  - however, if (se > elpd diff) then choose this model
- all "mod" = GAMMS
- all "mod_glm" = GLMMS

# coral

```{r}
loo_compare(brms::loo(coral_mod),
            brms::loo(coral_mod_glm)) # this model is better
``` 

- GLMM better

# macroalgae

```{r}
loo_compare(brms::loo(ma_mod), # this model is better
            brms::loo(ma_mod_glm)) 
``` 

- GAMM better

# turf algae

```{r}
loo_compare(brms::loo(ta_mod), 
            brms::loo(ta_mod_glm)) # this model is better 
``` 

- GLMM better

# octocoral

```{r}
loo_compare(brms::loo(oct_mod), 
            brms::loo(oct_mod_glm)) # this model is better 
``` 

- GLMM better

# rock

```{r}
loo_compare(brms::loo(rock_mod), 
            brms::loo(rock_mod_glm)) # this model is better 
``` 

- GLMM better

# unconsolidated substrate

```{r}
loo_compare(brms::loo(us_mod), 
            brms::loo(us_mod_glm)) # this model is better 
``` 

-GLMM better