---
title: "Data_prep"
format: html
editor: visual
---

# load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
#source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# read csv

## benthic file

```{r}
benthic_master <- read_csv("ROV_Relief_Slope_UPDATED.csv",
                           trim_ws = TRUE)

glimpse(benthic_master)
```
### find site names

- Site names in the benthic file will dictate what sites to include in the fish file

declare site as factor

```{r}
benthic_master <- 
  benthic_master |> 
  mutate(Site = factor(Site))
```

check levels of site

```{r}
benthic_sites <-
benthic_master |> 
  with(unique(Site)) |> 
  as.tibble() |> 
  rename(Benthic_site_names = value)
```
unique for survey

```{r}
benthic_surveys <-
benthic_master |> 
  with(unique(Survey)) |> 
  as.tibble() |> 
  rename(Benthic_survey = value)
```

## fish file

```{r}
fish_master <- read_csv("master_ROV_fish_Tim_2.csv",
                        trim_ws = TRUE)

#glimpse(fish_master)
```

declare site as factors

```{r}
fish_master <-
  fish_master |> 
  mutate(Site = factor(Site),
         Reef_1 = factor(Reef_1),
         Reef_2 = factor(Reef_2))
```

### check levels of survey

```{r}
fish_survey <-
fish_master |> 
  with(unique(Survey)) |> 
  as.tibble() |> 
  rename(Fish_survey = value)
```

- filter survey datas Feb_21, Jul_21, Feb_22

- filter only these dates as these dates had benthic surveys

```{r}
fish_master_v2 <- 
  fish_master |> 
  filter(Survey == "Feb_21" |
           Survey == "Jul_21" |
           Survey == "Feb_22")
```

###check levels of site

```{r}
fish_sites <-
fish_master_v2 |> 
  with(unique(Site)) |> 
  as.tibble() |> 
  rename(Fish_site_names = value)
```

# check site names manually

- problematic sites in benthic_master
  - Lihou_N1,
  - Lihou_S1,
  - Lihou_S2

```{r}
benthic_master |> 
  filter(Site == "Edna_2")
```
names for Lihou

```{r}
fish_master_v2 |> 
  filter(Reef_1 == "Lihou") |> 
  with(unique(Reef_2))
```

```{r}
fish_master_v2 |> 
  filter(Reef_2 == "Edna Cay") 
```
# filter out problematic sites and then rename the benthic site names

```{r}
benthic_master_v2 <-
  benthic_master |> 
    filter(Site != "Edna_2" &
           Site != "Edna_3" & 
           Site != "Lihou_N1" & 
           Site != "Lihou_S1" &
           Site != "Lihou_S2") |> 
  mutate(Site_recode = recode(Site,
                       BVille_1 = "BOUG-01",
                       Chilcott_1 = "CHIL-01",
                       Edna_1 = "EDNA-01",
                       Flinders_N1 = "FLIN-02",
                       Flinders_S1 = "FLIN-01",
                       Fred_W1 = "FRED-01",
                       Herald_1 = "HERA-01",
                       HerSurp_1 = "HSUP-01",
                       Holmes_2 = "HOLM-02",
                       Juliette_1 = "JULI-01",
                       Juliette_2 = "JULI-02",
                       Kenn_1 = "KENN-01",
                       Marion_1 = "MARI-01",
                       Osp_N1 = "OSPR-01",
                       Saumarez_S1 = "SAUM-01",
                       Willis_N1 = "WILL-01",
                       Wreck_E1 = "WREC-01"))
```

# check levels of site in benthic database after changing the names

- looks correct

```{r}
benthic_master_v2 |> 
  with(unique(Site_recode)) |> 
  as.tibble() |> 
  arrange(value)
```

# new T_ID for benthic and fish database (used for merging later)

```{r}
glimpse(benthic_master_v2)
```

```{r}
fish_master_v2 |> glimpse()
```
# New ID benthic

```{r}
benthic_master_v3 <- 
benthic_master_v2 |> 
  mutate(New_ID = factor(paste(Survey,
                               Site_recode,
                               Transect,
                               sep = "|")))
```

# New ID fish and filter only herbivore functional groups

```{r}
fish_master_v3 <-
fish_master_v2 |> 
  mutate(New_ID = factor(paste(Survey,
                               Site,
                               Transect,
                               sep = "|"))) |> 
  filter(Functional.Group == "browser" |
           Functional.Group == "cropper/grazer" |
           Functional.Group == "detritivore" |
           Functional.Group == "excavator" |
           Functional.Group == "scraper") |> 
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae")
```

# wide format with functional groups as column names and values as abundance

```{r}
fish_master_abun <- 
fish_master_v3 |> 
  pivot_wider(names_from = Functional.Group, 
              values_from = Number,
              values_fn = sum) |> 
  select(New_ID,
         Site,
         Transect,
         Depth_m,
         `cropper/grazer`,
         browser,
         detritivore,
         excavator,
         scraper) |> 
  rename(cropper = `cropper/grazer`) |> 
  mutate(across(cropper: scraper,
         ~replace_na(.x, 0)))
```

