---
title: "BC_Fish_Biom_Fits"
format: html
editor: visual
---

## load csv

```{r}
brt_bc_fishbiom <- read_csv("Data/relationship_fish_bio_ben.csv",
                           trim_ws = TRUE)

brt_bc_fishbiom_v2 <-
  brt_bc_fishbiom |> 
  filter(Depth_m >= 30)
```

## select relevant benthic and fish columns

```{r}
brt_bc_fishbiom_v3 <- 
  brt_bc_fishbiom_v2 |> 
 # mutate(total_octocoral = complex_octocoral + other_octocoral) |> 
  dplyr::select(Site,
                Depth_m,
                cropper,
                browser,
                detritivore,
                excavator, 
                scraper,
               #Benthic_Complexity,
                turf_algae,
                total_macroalgae,
                total_hard_coral) |> 
                #unconsolidated_subs,
                #total_octocoral,
                #rock) |> 
  mutate(total_herbs = cropper + browser + detritivore + excavator + scraper)
```

## eda biomass and macroalgae

```{r}
brt_bc_fishbiom_v3 |> 
  ggplot(aes(x = total_macroalgae,
             y = cropper)) +
  geom_point() +
  geom_smooth(method = "lm")
```

# TOTAL HERBIVORS

## def formula

```{r}
herbs_b_form <- bf(total_herbs ~ turf_algae +
                   total_macroalgae +
                     total_hard_coral + 
                   (1 | Site),
                 family = hurdle_lognormal())
```

## get prior

```{r}
get_prior(herbs_b_form, data = brt_bc_fishbiom_v3)
```

## examine data

```{r}
brt_bc_fishbiom_v3 |>
  #summarise(med = median(total_herbs),
   #         mad = mad(total_herbs))
  summarise(log_med = log(median(total_herbs)),
            log_mad = log(mad(total_herbs))) 
```

```{r}
0.5/0.2
```

## weakly informed priors

```{r}
herb_b_priors <- prior(normal(0.5, 0.2), class = "Intercept") +
  prior(normal(0, 3), class = "b") +
  prior(student_t(3, 0, 0.2), class = "sigma") +
  prior(student_t(3, 0, 0.2), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## prior only model

```{r}
#| cache: true
herbs_b_prior_mod <- brm(herbs_b_form,
                    data = brt_bc_fishbiom_v3,
                    prior = herb_b_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
herbs_b_prior_mod  |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
herbs_b_mod <- update(herbs_b_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
herbs_b_mod |> mcmc_plot(type = "trace")
# autocorr
herbs_b_mod |> mcmc_plot(type = "acf_bar")

# rhat
herbs_b_mod |> mcmc_plot(type = "rhat_hist")

# ess
herbs_b_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
herbs_b_resids <- make_brms_dharma_res(herbs_b_mod)

# qqplot
herbs_b_resids |> testUniformity()

# residplot
herbs_b_resids |> plotResiduals(quantreg = FALSE)

# testdisp
herbs_b_resids |> testDispersion()
```

# CROPPER

## def formula

```{r}
crop_b_form <- bf(cropper ~ turf_algae +
                   total_macroalgae +
                     total_hard_coral + 
                   (1 | Site),
                 family = hurdle_lognormal())
```

## examine data

```{r}
brt_bc_fishbiom_v3 |> 
  summarise(log_med = log(median(cropper)),
            log_mad = log(mad(cropper))) 
```

```{r}
1.9/1.5
```

## weakly informed priors

```{r}
crop_b_priors <- prior(normal(1.9, 1.5), class = "Intercept") +
  prior(normal(0, 1.3), class = "b") +
  prior(student_t(3, 0, 1.5), class = "sigma") +
  prior(student_t(3, 0, 1.5), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## prior only model

```{r}
#| cache: true
crop_b_prior_mod <- brm(crop_b_form,
                    data = brt_bc_fishbiom_v3,
                    prior = crop_b_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
crop_b_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
crop_b_mod <- update(crop_b_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
crop_b_mod |> mcmc_plot(type = "trace")
# autocorr
crop_b_mod |> mcmc_plot(type = "acf_bar")

# rhat
crop_b_mod |> mcmc_plot(type = "rhat_hist")

# ess
crop_b_mod|> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
crop_b_resids <- make_brms_dharma_res(crop_b_mod)

# qqplot
crop_b_resids |> testUniformity()

# residplot
crop_b_resids |> plotResiduals()

# testdisp
#crop_b_resids |> testDispersion()
```

# DETRITIVORE

## def formula

```{r}
det_b_form <- bf(detritivore ~ turf_algae +
                   total_macroalgae +
                     total_hard_coral + 
                   (1 | Site),
                 family = hurdle_lognormal())
```

## examine data

```{r}
brt_bc_fishbiom_v3 |> 
  summarise(log_med = log(mean(detritivore)),
            log_mad = log(sd(detritivore))) 
```

```{r}
1.8/1.1
```

## weakly informed priors

```{r}
det_b_priors <- prior(normal(1.8, 1.1), class = "Intercept") +
  prior(normal(0, 1.6), class = "b") +
  prior(student_t(3, 0, 1.1), class = "sigma") +
  prior(student_t(3, 0, 1.1), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## prior only model

```{r}
#| cache: true
det_b_prior_mod <- brm(det_b_form,
                    data = brt_bc_fishbiom_v3,
                    prior = det_b_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
det_b_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
det_b_mod <- update(det_b_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
det_b_mod |> mcmc_plot(type = "trace")
# autocorr
det_b_mod |> mcmc_plot(type = "acf_bar")

# rhat
det_b_mod |> mcmc_plot(type = "rhat_hist")

# ess
det_b_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
det_b_resids <- make_brms_dharma_res(det_b_mod)

# qqplot
det_b_resids |> testUniformity()

# residplot
det_b_resids |> plotResiduals()

# testdisp
#crop_b_resids |> testDispersion()
```

# SCRAPERS

## def formula

```{r}
scra_b_form <- bf(scraper ~ turf_algae +
                   total_macroalgae +
                     total_hard_coral + 
                   (1 | Site),
                 family = hurdle_lognormal())
```

## examine data

```{r}
brt_bc_fishbiom_v3 |> 
  summarise(log_med = log(mean(scraper)),
            log_mad = log(sd(scraper))) 
```

```{r}
0.7/0.1
```

## weakly informed priors

```{r}
scra_b_priors <- prior(normal(0.7, 0.1), class = "Intercept") +
  prior(normal(0, 7), class = "b") +
  prior(student_t(3, 0, 0.1), class = "sigma") +
  prior(student_t(3, 0, 0.1), class = "sd") +
  prior(beta(1, 1), class = "hu")
```

## prior only model

```{r}
#| cache: true
scra_b_prior_mod <- brm(scra_b_form,
                    data = brt_bc_fishbiom_v3,
                    prior = scra_b_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
scra_b_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
scra_b_mod <- update(scra_b_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
scra_b_mod |> mcmc_plot(type = "trace")
# autocorr
scra_b_mod |> mcmc_plot(type = "acf_bar")

# rhat
scra_b_mod |> mcmc_plot(type = "rhat_hist")

# ess
scra_b_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
scra_b_resids <- make_brms_dharma_res(scra_b_mod)

# qqplot
scra_b_resids |> testUniformity()

# residplot
scra_b_resids |> plotResiduals()

# testdisp
#crop_b_resids |> testDispersion()
```
