---
title: "BC_Fish_Biom_Fits_Version2"
format: html
editor: visual
---

# TOTAL HERBIVORES

## summary table

```{r}
herbs_b_mod_v2 |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## ta_newdata

```{r}
ta_bio_newdata <- with(bc_fishbiom_v3,
                 data.frame(turf_algae = seq(min(turf_algae),
                                          max(turf_algae),
                                          length = 100)))
```

## predict ta change

```{r}
herb_ta_b_pred <- herbs_b_mod_v2 |> 
  emmeans(~ turf_algae, 
          at = ta_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-ta

```{r}
f3_p9 <- 
herb_ta_b_pred |> 
  ggplot(aes(y = median,
             x = turf_algae)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = total_herbs),
             size = 2.5, 
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#929FBD") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  scale_x_continuous(name = "Percentage cover") +
  ggtitle("P = 0.92") +
  scale_y_continuous(limits = c(0,80),
                     breaks = seq(0, 80, by = 20))
```

## ma_newdata

```{r}
ma_bio_newdata <- with(bc_fishbiom_v3,
                 data.frame(total_macroalgae = seq(min(total_macroalgae),
                                          max(total_macroalgae),
                                          length = 100)))
```

## predict ma change

```{r}
herb_ma_b_pred <- herbs_b_mod_v2 |> 
  emmeans(~ total_macroalgae, 
          at = ma_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-ma

```{r}
f3_p8 <- 
herb_ma_b_pred |> 
  ggplot(aes(y = median,
             x = total_macroalgae)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = total_herbs),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  scale_x_continuous(name = "Percentage cover") +
  ggtitle("P = 0.99") +
  scale_y_continuous(limits = c(0,80),
                     breaks = seq(0, 80, by = 20))
```

## hc_newdata

```{r}
hc_bio_newdata <- with(bc_fishbiom_v3,
                 data.frame(total_hard_coral = seq(min(total_hard_coral),
                                          max(total_hard_coral),
                                          length = 100)))
```

## predict hc change

```{r}
herb_hc_b_pred <- herbs_b_mod_v2 |> 
  emmeans(~ total_hard_coral, 
          at = hc_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-hc

```{r}
f3_p7 <- 
herb_hc_b_pred |> 
  ggplot(aes(y = median,
             x = total_hard_coral)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = total_herbs),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  theme_classic() +
 # theme(axis.title.y = element_blank(),
  #      axis.ticks.y = element_blank(),
   #     axis.text.y = element_blank()) +
  scale_x_continuous(name = "Percentage cover") +
  scale_y_continuous(name = "Total biomass",
                    limits = c(0,80),
                     breaks = seq(0, 80, by = 20)) +
  ggtitle("P = 0.99")
```

# CROPPERS

## summary table

```{r}
crop_b_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict ta change

```{r}
crop_ta_b_pred <- crop_b_mod |> 
  emmeans(~ turf_algae, 
          at = ta_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-ta

```{r}
f5_p3 <- 
crop_ta_b_pred |> 
  ggplot(aes(y = median,
             x = turf_algae)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = cropper),
             size = 2.5, 
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#929FBD") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  theme_classic() +
  scale_y_continuous(
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("Turf algae 
P = 0.85")
```

## predict ma change

```{r}
crop_ma_b_pred <- crop_b_mod |> 
  emmeans(~ total_macroalgae, 
          at = ma_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-ma

```{r}
f5_p2 <- 
crop_ma_b_pred |> 
  ggplot(aes(y = median,
             x = total_macroalgae)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = cropper),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  theme_classic() +
  scale_y_continuous(
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("Macroalgae 
P = 0.98")
```

## predict hc change

```{r}
crop_hc_b_pred <- crop_b_mod |> 
  emmeans(~ total_hard_coral, 
          at = hc_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-hc

```{r}
f5_p1 <- 
crop_hc_b_pred  |> 
  ggplot(aes(y = median,
             x = total_hard_coral)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = cropper),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  scale_x_continuous(name = "Percentage cover") +
  scale_y_continuous(name = "Cropper biomass",
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) + 
  ggtitle("Hard coral 
P = 0.98")
```

# DETRITIVORE

## summary table

```{r}
det_b_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict ta change

```{r}
det_ta_b_pred <- det_b_mod |> 
  emmeans(~ turf_algae, 
          at = ta_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-ta

```{r}
f5_p6 <- 
det_ta_b_pred |> 
  ggplot(aes(y = median,
             x = turf_algae)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = detritivore),
             size = 2.5, 
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#929FBD") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  theme_classic() +
  scale_y_continuous(
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("P = 0.57")
```

## predict ma change

```{r}
det_ma_b_pred <- det_b_mod |> 
  emmeans(~ total_macroalgae, 
          at = ma_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```


## plot bio-ma

```{r}
f5_p5 <- 
det_ma_b_pred |> 
  ggplot(aes(y = median,
             x = total_macroalgae)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = detritivore),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  theme_classic() +
  scale_y_continuous(
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("P = 0.56")
```

## predict hc change

```{r}
det_hc_b_pred <- det_b_mod |> 
  emmeans(~ total_hard_coral, 
          at = hc_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-hc

```{r}
f5_p4 <- 
det_hc_b_pred |> 
  ggplot(aes(y = median,
             x = total_hard_coral)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = detritivore),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  theme_classic()  +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  #scale_x_continuous(name = "Percentage cover") +
  scale_y_continuous(name = "Detritivore biomass",
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) + 
   ggtitle("P = 0.50")
```

# SCAPER

## summary table

```{r}
scra_b_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict ta change

```{r}
scra_ta_b_pred <- scra_b_mod |> 
  emmeans(~ turf_algae, 
          at = ta_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-ta

```{r}
f5_p9 <- 
scra_ta_b_pred |> 
  ggplot(aes(y = median,
             x = turf_algae)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = scraper),
             size = 2.5, 
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#929FBD") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  theme_classic() +
  scale_y_continuous(
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  scale_x_continuous(name = "Percentage cover") +
  ggtitle("P = 0.76")
```

## predict ma change

```{r}
scra_ma_b_pred <- scra_b_mod |> 
  emmeans(~ total_macroalgae, 
          at = ma_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-ma

```{r}
f5_p8 <- 
scra_ma_b_pred |> 
  ggplot(aes(y = median,
             x = total_macroalgae)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = scraper),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  theme_classic() +
  scale_y_continuous(
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  scale_x_continuous(name = "Percentage cover") +
  ggtitle("P = 0.82")
```

## predict hc change

```{r}
scra_hc_b_pred <- scra_b_mod |> 
  emmeans(~ total_hard_coral, 
          at = hc_bio_newdata, 
          type = "link") |> 
  gather_emmeans_draws() |> 
  mutate(Exp_sprich = exp(.value)) |> 
  dplyr::select(-.chain,
                -.iteration,
                -.value) |> 
  summarise_draws(median, 
                  HDInterval::hdi) |> 
  as.data.frame()
```

## plot bio-hc

```{r}
f5_p7 <- 
scra_hc_b_pred |> 
  ggplot(aes(y = median,
             x = total_hard_coral)) +
   geom_point(data = bc_fishbiom_v3,
             aes(y = scraper),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  theme_classic() +
 # theme(axis.title.y = element_blank(),
  #      axis.ticks.y = element_blank(),
   #     axis.text.y = element_blank()) +
  scale_x_continuous(name = "Percentage cover")  +
  scale_y_continuous(name = "Scraper biomass",
                     limits = c(0,15),
                     breaks = seq(0, 15, by = 5)) + 
  ggtitle("P = 0.75")
```

# TOTAL HERBIVORES: Compile plots

```{r}
f3_bc_total_herbs <- 
(f3_p1 + f3_p2 + f3_p3) /
(f3_p4 + f3_p5 + f3_p6) /
  (f3_p7 + f3_p8 + f3_p9)
```

## ggsave

```{r}
ggsave("Fig. 3. bc_total_herbs.jpeg",
       plot = f3_bc_total_herbs, 
       dpi = 600, 
       height = 7.5, 
       width = 7.5, 
       units = "in")
```

# FG BIOMASS: compile plots

```{r}
p_fg_biomass <- 
(f5_p1 + f5_p2 + f5_p3) /
(f5_p4 + f5_p5 + f5_p6) /
  (f5_p7 + f5_p8 + f5_p9)
```

## ggsave

```{r}
ggsave("Fig. 5. bc_fg_biom.jpeg",
       plot = p_fg_biomass, 
       dpi = 600, 
       height = 7.5, 
       width = 7.5, 
       units = "in")
```