---
title: "EDA_Benthic_Cover"
format: html
editor: visual
---

# load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# read csv

```{r}
benthic <- read_csv("Data/db_benthic.csv",
                           trim_ws = TRUE)
```
# mutate to create total octocoral

```{r}
benthic <- 
  benthic |> 
  mutate(total_octocoral = complex_octocoral + other_octocoral)
```


# EDA

## Depth total_hard_coral

- Nonlinear relationship with depth

```{r}
benthic |> 
ggplot(aes(x = Depth,
           y = total_hard_coral)) +
  geom_point() +
  geom_smooth(method = "gam") +
  theme_classic()
```

## Depth total_macroalgae (macroalgae and Halimeda combined)

- Nonlinear relationship with depth

```{r}
`benthic |> 
ggplot(aes(x = Depth,
           y = total_macroalgae)) +
  geom_point() +
  geom_smooth(method = "gam") +
  theme_classic()`
```

## Depth macroalgae (excluding Halimeda)

- Nonlinear relationship with depth

```{r}
benthic |> 
ggplot(aes(x = Depth,
           y = macroalgae)) +
  geom_point() +
  geom_smooth(method = "gam") +
  theme_classic()
```

## Depth turf_algae

- Nonlinear relationship with depth

```{r}
benthic |> 
ggplot(aes(x = Depth,
           y = turf_algae)) +
  geom_point() +
  geom_smooth(method = "gam") +
  theme_classic()
```

## Depth unconsolidated_subs

```{r}
benthic |> 
ggplot(aes(x = Depth,
           y = unconsolidated_subs)) +
  geom_point() +
  geom_smooth(method = "gam") +
  theme_classic()
```

## Depth rock

- Linear or Non-linear relationship with depth

```{r}
benthic |> 
ggplot(aes(x = Depth,
           y = rock)) +
  geom_point() +
  geom_smooth(method = "gam") +
  theme_classic()
```

## Depth total_octocoral

- Looks more linear than a GAM

```{r}
benthic |> 
ggplot(aes(x = Depth,
           y = total_octocoral)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```

# Variables of interest

- hard coral (total)
- macroalgae (total)
- turf algae (total)
- octocoral (total)
- rock
- unconsolidated substrate

### Depth Halimeda

- No clear pattern

```{r}
benthic |> 
ggplot(aes(x = Depth,
           y = halimeda)) +
  geom_point() +
  geom_smooth(method = "gam") +
  theme_classic()
```

### Depth cca (too many zeroes)

```{r}
benthic |> 
ggplot(aes(x = Depth,
           y = cca)) +
  geom_point() +
  #geom_smooth(method = "gam") +
  theme_classic()
```
