---
title: "BC_Fish_Abun_Fits_2"
format: html
editor: visual
---

# library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

## load csv

```{r}
brt_bc_fishab <- read_csv("Data/relationship_fish_ab_ben_version2.csv",
                           trim_ws = TRUE)

brt_bc_fishab_v2 <-
  brt_bc_fishab |> 
  filter(Depth_m >= 30)
```


## select relevant benthic and fish columns

```{r}
brt_bc_fishab_v3 <- 
  brt_bc_fishab_v2 |> 
  mutate(total_octocoral = complex_octocoral + other_octocoral) |> 
  dplyr::select(Site,
                Depth_m,
                cropper,
                browser,
                detritivore,
                excavator, 
                scraper,
                Benthic_Complexity,
                turf_algae,
                total_macroalgae,
                total_hard_coral,
                unconsolidated_subs,
                total_octocoral,
                rock) |> 
  mutate(total_herbs = cropper + browser + detritivore + excavator + scraper)
```

## eda total_hard_coral and Benthic_Complexity

```{r}
brt_bc_fishab_v3 |> 
  ggplot(aes(x = Benthic_Complexity,
             y = scale(total_hard_coral))) +
  geom_point() +
  geom_smooth(method = "lm")
```

- Variables seemed correlated so decided to just use HC

# TOTAL HERBIVORS

## def formula

```{r}
herbs_form_v2 <- bf(total_herbs ~ turf_algae +
                   total_macroalgae +
                     total_hard_coral + 
                   (1 | Site),
                 family = negbinomial())
```

## weakly informed priors

```{r}
herb_priors_v2 <- prior(normal(1.3, 1.5), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1.5), class = "sd")
```

## prior only model

```{r}
#| cache: true
herbs_prior_mod_v2 <- brm(herbs_form_v2,
                    data = brt_bc_fishab_v3,
                    prior = herb_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
herbs_prior_mod_v2 |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
herbs_mod_v2 <- update(herbs_prior_mod_v2,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
herbs_mod_v2 |> mcmc_plot(type = "trace")
# autocorr
herbs_mod_v2 |> mcmc_plot(type = "acf_bar")

# rhat
herbs_mod_v2 |> mcmc_plot(type = "rhat_hist")

# ess
herbs_mod_v2 |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
herbs_resids_v2 <- make_brms_dharma_res(herbs_mod_v2)

# qqplot
herbs_resids_v2 |> testUniformity()

# residplot
herbs_resids_v2 |> plotResiduals()

# testdisp
herbs_resids_v2 |> testDispersion()
```

# CROPPER

## def formula

```{r}
crop_form_v2 <- bf(cropper ~ turf_algae +
                   total_macroalgae +
                     total_hard_coral + 
                   (1 | Site),
                 family = negbinomial())
```

## weakly informed priors

```{r}
crop_priors_v2 <- prior(normal(0.7, 1), class = "Intercept") +
  prior(normal(0, 0.7), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

## prior only model

```{r}
#| cache: true
crop_prior_mod_v2 <- brm(crop_form_v2,
                    data = brt_bc_fishab_v3,
                    prior = crop_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
crop_prior_mod_v2 |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
crop_mod_v2 <- update(crop_prior_mod_v2,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
crop_mod_v2 |> mcmc_plot(type = "trace")
# autocorr
crop_mod_v2 |> mcmc_plot(type = "acf_bar")

# rhat
crop_mod_v2 |> mcmc_plot(type = "rhat_hist")

# ess
crop_mod_v2 |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
crop_resids_v2 <- make_brms_dharma_res(crop_mod_v2)

# qqplot
crop_resids_v2 |> testUniformity()

# residplot
crop_resids_v2 |> plotResiduals()

# testdisp
crop_resids_v2 |> testDispersion()
```

# DETRITIVORES

## def formula

```{r}
det_form_v2 <- bf(detritivore ~ turf_algae +
                   total_macroalgae +
                     total_hard_coral + 
                   (1 | Site),
                 family = negbinomial())
```

## weakly informed priors

```{r}
det_priors_v2 <- prior(normal(0.5, 1), class = "Intercept") +
  prior(normal(0, 0.5), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

## prior only model

```{r}
#| cache: true
det_prior_mod_v2 <- brm(det_form_v2,
                    data = brt_bc_fishab_v3,
                    prior = det_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## fit the model

```{r}
#| cache: true
det_mod_v2 <- update(det_prior_mod_v2,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
det_mod_v2 |> mcmc_plot(type = "trace")
# autocorr
det_mod_v2 |> mcmc_plot(type = "acf_bar")

# rhat
det_mod_v2 |> mcmc_plot(type = "rhat_hist")

# ess
det_mod_v2 |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
det_resids_v2 <- make_brms_dharma_res(det_mod_v2)

# qqplot
det_resids_v2 |> testUniformity()

# residplot
det_resids_v2 |> plotResiduals()

# testdisp
det_resids_v2 |> testDispersion()
```

# SCRAPERS

## def formula

```{r}
scra_form_v2 <- bf(scraper ~ turf_algae +
                   total_macroalgae +
                     total_hard_coral + 
                   (1 | Site),
                 family = negbinomial())
```

## weakly informed priors

```{r}
scra_priors_v2 <- prior(normal(0.1, 0.3), class = "Intercept") +
  prior(normal(0, 0.3), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 0.3), class = "sd")
```

## prior only model

```{r}
#| cache: true
scra_prior_mod_v2 <- brm(scra_form_v2,
                    data = brt_bc_fishab_v3,
                    prior = scra_priors_v2,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## fit the model

```{r}
#| cache: true
scra_mod_v2 <- update(scra_prior_mod_v2,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
scra_mod_v2  |> mcmc_plot(type = "trace")
# autocorr
scra_mod_v2  |> mcmc_plot(type = "acf_bar")

# rhat
scra_mod_v2  |> mcmc_plot(type = "rhat_hist")

# ess
scra_mod_v2 |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
scra_resids_v2 <- make_brms_dharma_res(scra_mod_v2)

# qqplot
scra_resids_v2 |> testUniformity()

# residplot
scra_resids_v2 |> plotResiduals()

# testdisp
scra_resids_v2 |> testDispersion()
```