---
title: "BC_Fish_Abun_Results_Plots"
format: html
editor: visual
---

# TOTAL HERBIVORES

## summary table

```{r}
herbs_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

-   evidence for octocoral (0.89)

## oct_newdata

```{r}
oct_newdata <- with(brt_bc_fishab_v3,
                 data.frame(total_octocoral = seq(min(total_octocoral),
                                          max(total_octocoral),
                                          length = 100)))
```

## predict octocoral change

```{r}
herb_oct_pred <- herbs_mod |> 
  emmeans(~ total_octocoral, 
          at = oct_newdata, 
          type = "response") |> 
  as.data.frame()

glimpse(herb_oct_pred)
```

## herbs-oct plot

```{r}
herb_oct_pred |> 
  ggplot(aes(y = prob,
             x = total_octocoral)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = total_herbs),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 25)) +
  scale_x_continuous(name = "Octocoral cover (%)") +
  ggtitle("Total herbivores") +
  theme_classic()
```

# CROPPERS

## summary table

```{r}
crop_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

-   no evidence for all

## NO plots for CROPPERS because no evidence for anything

# DETRITIVORES

## summary table

```{r}
det_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

-   evidence octocoral

## oct_newdata

```{r}
oct_newdata <- with(brt_bc_fishab_v3,
                 data.frame(total_octocoral = seq(min(total_octocoral),
                                          max(total_octocoral),
                                          length = 100)))
```

## predict octocoral change

```{r}
det_oct_pred <- det_mod |> 
  emmeans(~ total_octocoral, 
          at = oct_newdata, 
          type = "response") |> 
  as.data.frame()

#glimpse(det_oct_pred)
```

## det-oct plot

```{r}
det_oct_pred |> 
  ggplot(aes(y = prob,
             x = total_octocoral)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = detritivore),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 25)) +
  scale_x_continuous(name = "Octocoral cover (%)") +
  ggtitle("Detritivores") +
  theme_classic()
```

# SCRAPERS

## summary table

```{r}
scra_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

-   evidence octocoral
-   evidence hard coral

## oct_newdata

```{r}
oct_newdata <- with(brt_bc_fishab_v3,
                 data.frame(total_octocoral = seq(min(total_octocoral),
                                          max(total_octocoral),
                                          length = 100)))
```

## hc_newdata

```{r}
hc_newdata <- with(brt_bc_fishab_v3,
                 data.frame(total_hard_coral = seq(min(total_hard_coral),
                                          max(total_hard_coral),
                                          length = 100)))
```

## predict octocoral change

```{r}
scra_oct_pred <- scra_mod |> 
  emmeans(~ total_octocoral, 
          at = oct_newdata, 
          type = "response") |> 
  as.data.frame()

#glimpse(det_oct_pred)
```

## scra-oct plot

```{r}
scra_oct_pred |> 
  ggplot(aes(y = prob,
             x = total_octocoral)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = scraper),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 25)) +
  scale_x_continuous(name = "Octocoral cover (%)") +
  ggtitle("Scapers") +
  theme_classic()
```

## predict hard coral change

```{r}
scra_hc_pred <- scra_mod |> 
  emmeans(~ total_hard_coral, 
          at = hc_newdata, 
          type = "response") |> 
  as.data.frame()

#glimpse(det_oct_pred)
```

## scra-hc plot

```{r}
scra_hc_pred |> 
  ggplot(aes(y = prob,
             x = total_hard_coral)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = scraper),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                       limits = c(0, 50),
  breaks = seq(0, 50, by = 25)) +
  scale_x_continuous(name = "Hard coral cover (%)") +
  ggtitle("Scapers") +
  theme_classic()
```
