---
title: "BC_Fish_Abun_fits"
format: html
editor: visual
---

# library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# data prep

## load csv

```{r}
brt_bc_fishab <- read_csv("Data/relationship_fish_ab_ben.csv",
                           trim_ws = TRUE)

brt_bc_fishab_v2 <-
  brt_bc_fishab |> 
  filter(Depth_m >= 30)
```

## select relevant benthic and fish columns

```{r}
brt_bc_fishab_v3 <- 
  brt_bc_fishab_v2 |> 
  mutate(total_octocoral = complex_octocoral + other_octocoral) |> 
  dplyr::select(Site,
                Depth_m,
                cropper,
                browser,
                detritivore,
                excavator, 
                scraper,
                Benthic_Complexity,
                turf_algae,
                total_macroalgae,
                total_hard_coral,
                unconsolidated_subs,
                total_octocoral,
                rock) |> 
  mutate(total_herbs = cropper + browser + detritivore + excavator + scraper)
```

## view data and remove nas

```{r}
brt_bc_fishab_v3 <-
brt_bc_fishab_v3 |> 
  drop_na()

brt_bc_fishab_v3 |> glimpse()
```

# TOTAL HERBIVORES

## eda

```{r}
brt_bc_fishab_v3 |> 
  ggplot(aes(x = total_octocoral,
             y = total_herbs)) +
  geom_point() +
  geom_smooth()
```

-   us and total herbs: looks linear
-   oct and total herbs: looks linear

## def formula

```{r}
herbs_form <- bf(total_herbs ~ unconsolidated_subs +
                   total_octocoral +
                   (1 | Site),
                 family = negbinomial())
```

## examine data

```{r}
brt_bc_fishab_v3 |> 
  summarise(log_med = log(median(total_herbs)),
            log_mad = log(mad(total_herbs))) 
```

```{r}
1.3/1.5
```

## weakly informed priors

```{r}
herb_priors <- prior(normal(1.3, 1.5), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1.5), class = "sd")
```

## prior only model

```{r}
#| cache: true
herbs_prior_mod <- brm(herbs_form,
                    data = brt_bc_fishab_v3,
                    prior = herb_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
herbs_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
herbs_mod <- update(herbs_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## partial plots

```{r}
herbs_mod |> 
  conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots()
```

## MCMC diagnostics

```{r}
# trace
herbs_mod |> mcmc_plot(type = "trace")
# autocorr
herbs_mod |> mcmc_plot(type = "acf_bar")

# rhat
herbs_mod |> mcmc_plot(type = "rhat_hist")

# ess
herbs_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
herbs_resids <- make_brms_dharma_res(herbs_mod)

# qqplot
herbs_resids |> testUniformity()

# residplot
herbs_resids |> plotResiduals()

# testdisp
herbs_resids |> testDispersion()
```

# CROPPERS

## eda

```{r}
brt_bc_fishab_v3 |> 
  ggplot(aes(x = unconsolidated_subs,
             y = cropper)) +
  geom_point() +
  geom_smooth(method = "lm")
```

-   us and total herbs: looks linear
-   oct and total herbs: looks linear

## def formula

```{r}
crop_form <- bf(cropper ~ unconsolidated_subs +
                   total_octocoral +
                  total_hard_coral +
                   (1 | Site),
                 family = negbinomial())
```

## examine data

```{r}
brt_bc_fishab_v3 |> 
  summarise(log_med = log(median(cropper)),
            log_mad = log(mad(cropper))) 
```

```{r}
0.7/1
```

## weakly informed priors

```{r}
crop_priors <- prior(normal(0.7, 1), class = "Intercept") +
  prior(normal(0, 0.7), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

## prior only model

```{r}
#| cache: true
crop_prior_mod <- brm(crop_form,
                    data = brt_bc_fishab_v3,
                    prior = crop_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
crop_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
crop_mod <- update(crop_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
crop_mod |> mcmc_plot(type = "trace")
# autocorr
crop_mod |> mcmc_plot(type = "acf_bar")

# rhat
crop_mod |> mcmc_plot(type = "rhat_hist")

# ess
crop_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
crop_resids <- make_brms_dharma_res(crop_mod)

# qqplot
crop_resids |> testUniformity()

# residplot
crop_resids |> plotResiduals()

# testdisp
crop_resids |> testDispersion()
```

# DETRITIVORE

## eda

```{r}
brt_bc_fishab_v3 |> 
  ggplot(aes(x = total_macroalgae,
             y = detritivore)) +
  geom_point() +
  geom_smooth(method = "lm")
```

-   ma and total herbs: looks linear
-   oct and total herbs: looks linear

## def formula

```{r}
det_form <- bf(detritivore ~ total_macroalgae +
                   total_octocoral +
                   (1 | Site),
                 family = negbinomial())
```

## examine data

```{r}
brt_bc_fishab_v3 |> 
  summarise(log_med = log(mean(detritivore)),
            log_mad = log(sd(detritivore))) 
```

```{r}
0.5/1
```

## weakly informed priors

```{r}
det_priors <- prior(normal(0.5, 1), class = "Intercept") +
  prior(normal(0, 0.5), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1), class = "sd")
```

## prior only model

```{r}
#| cache: true
det_prior_mod <- brm(det_form,
                    data = brt_bc_fishab_v3,
                    prior = det_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
det_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
det_mod <- update(det_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
det_mod |> mcmc_plot(type = "trace")
# autocorr
det_mod |> mcmc_plot(type = "acf_bar")

# rhat
det_mod |> mcmc_plot(type = "rhat_hist")

# ess
det_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
det_resids <- make_brms_dharma_res(det_mod)

# qqplot
det_resids |> testUniformity()

# residplot
det_resids |> plotResiduals()

# testdisp
det_resids |> testDispersion()
```

# SCRAPERS

## eda

```{r}
brt_bc_fishab_v3 |> 
  ggplot(aes(x = rock,
             y = scraper)) +
  geom_point() +
  geom_smooth(method = "lm")
```

-   ma and total herbs: looks linear
-   oct and total herbs: looks linear

## def formula

```{r}
scra_form <- bf(scraper ~ total_hard_coral +
                   total_octocoral +
                  rock + 
                   (1 | Site),
                 family = negbinomial())
```

## examine data

```{r}
brt_bc_fishab_v3 |> 
  summarise(log_med = log(mean(scraper)),
            log_mad = log(sd(scraper))) 
```

```{r}
0.13/0.36
```

## weakly informed priors

```{r}
scra_priors <- prior(normal(0.1, 0.3), class = "Intercept") +
  prior(normal(0, 0.3), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 0.3), class = "sd")
```

## prior only model

```{r}
#| cache: true
scra_prior_mod <- brm(scra_form,
                    data = brt_bc_fishab_v3,
                    prior = scra_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## prior eval

```{r}
scra_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## fit the model

```{r}
#| cache: true
scra_mod <- update(scra_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
scra_mod  |> mcmc_plot(type = "trace")
# autocorr
scra_mod  |> mcmc_plot(type = "acf_bar")

# rhat
scra_mod  |> mcmc_plot(type = "rhat_hist")

# ess
scra_mod |> mcmc_plot(type = "neff_hist")
```

## residuals

```{r}
scra_resids <- make_brms_dharma_res(scra_mod)

# qqplot
scra_resids |> testUniformity()

# residplot
scra_resids|> plotResiduals()

# testdisp
scra_resids |> testDispersion()
```
