---
title: "BC_Fish_Abun_Results_Plots_Version2"
format: html
editor: visual
---

-   csv dataset used: brt_bc_fishab_v3
-   insert exceedence probs for all the plots

# TOTAL HERBIVORES

## summary table

```{r}
herbs_mod_v2  |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## ta_newdata

```{r}
ta_ab_newdata <- with(brt_bc_fishab_v3,
                 data.frame(turf_algae = seq(min(turf_algae),
                                          max(turf_algae),
                                          length = 100)))
```

## predict ta change

```{r}
herb_ta_pred <- herbs_mod_v2 |> 
  emmeans(~ turf_algae, 
          at = ta_ab_newdata, 
          type = "response") |> 
  as.data.frame()

herb_ta_pred |> head()
```

## herbs-ta plot

```{r}
f3_p6 <-
herb_ta_pred |> 
  ggplot(aes(y = prob,
             x = turf_algae)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = total_herbs),
             size = 2.5, 
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#929FBD") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("P = 0.73") +
  scale_y_continuous(limits = c(0,50),
                     breaks = seq(0, 50, by = 10))
```

## ma_newdata

```{r}
ma_ab_newdata <- with(brt_bc_fishab_v3,
                 data.frame(total_macroalgae = seq(min(total_macroalgae),
                                          max(total_macroalgae),
                                          length = 100)))
```

## predict ma change

```{r}
herb_ma_pred <- herbs_mod_v2 |> 
  emmeans(~ total_macroalgae, 
          at = ma_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## herbs-ma plot

```{r}
f3_p5 <-
herb_ma_pred |> 
  ggplot(aes(y = prob,
             x = total_macroalgae)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = total_herbs),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("P = 0.96") +
  scale_y_continuous(limits = c(0,50),
                     breaks = seq(0, 50, by = 10))
```

## hc_newdata

```{r}
hc_ab_newdata <- with(brt_bc_fishab_v3,
                 data.frame(total_hard_coral = seq(min(total_hard_coral),
                                          max(total_hard_coral),
                                          length = 100)))
```

## predict hc change

```{r}
herb_hc_pred <- herbs_mod_v2 |> 
  emmeans(~ total_hard_coral, 
          at = hc_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## herbs-hc plot

```{r}
f3_p4 <- 
herb_hc_pred |> 
  ggplot(aes(y = prob,
             x = total_hard_coral)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = total_herbs),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  scale_y_continuous(name = "Total abundance",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  ggtitle("P = 0.93") 
```

# CROPPERS

## summary table

```{r}
crop_mod_v2 |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict ta change

```{r}
crop_ta_pred <- crop_mod_v2  |> 
  emmeans(~ turf_algae, 
          at = ta_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## crop-ta plot

```{r}
f4_p3 <-
crop_ta_pred |> 
  ggplot(aes(y = prob,
             x = turf_algae)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = cropper),
             size = 2.5, 
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#929FBD") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("Turf algae
P = 0.82") +
  scale_y_continuous(limits = c(0,40),
                     breaks = seq(0,40,by = 10))
```

## predict ma change

```{r}
crop_ma_pred <- crop_mod_v2  |> 
  emmeans(~ total_macroalgae, 
          at = ma_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## crop-ma plot

```{r}
f4_p2 <- 
crop_ma_pred |> 
  ggplot(aes(y = prob,
             x = total_macroalgae)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = cropper),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("Macroalgae
P = 0.95") +
  scale_y_continuous(limits = c(0,40),
                     breaks = seq(0,40,by = 10))
```

## predict hc change

```{r}
crop_hc_pred <- crop_mod_v2  |> 
  emmeans(~ total_hard_coral, 
          at = hc_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## crop-hc plot

```{r}
f4_p1 <-
crop_hc_pred |> 
  ggplot(aes(y = prob,
             x = total_hard_coral)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = cropper),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  scale_y_continuous(name = "Cropper abundance",
                     limits = c(0,40),
                     breaks = seq(0,40,by = 10)) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  ggtitle("Hard coral
P = 0.89") 
```

# DETRITIVORES

## summary table

```{r}
det_mod_v2 |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict ta change

```{r}
det_ta_pred <- det_mod_v2  |> 
  emmeans(~ turf_algae, 
          at = ta_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## det-ta plot

```{r}
f4_p6 <-
det_ta_pred |> 
  ggplot(aes(y = prob,
             x = turf_algae)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = detritivore),
             size = 2.5, 
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#929FBD") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("P = 0.59") +
  scale_y_continuous(limits = c(0,40),
                     breaks = seq(0,40,by = 10))
```

## predict ma change

```{r}
det_ma_pred <- det_mod_v2  |> 
  emmeans(~ total_macroalgae, 
          at = ma_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## det-ma plot

```{r}
f4_p5 <- 
det_ma_pred |> 
  ggplot(aes(y = prob,
             x = total_macroalgae)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = detritivore),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  ggtitle("P = 0.68") +
  scale_y_continuous(limits = c(0,40),
                     breaks = seq(0,40,by = 10))
```

## predict hc change

```{r}
det_hc_pred <- det_mod_v2 |> 
  emmeans(~ total_hard_coral, 
          at = hc_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## det-hc plot

```{r}
f4_p4 <-
det_hc_pred |> 
  ggplot(aes(y = prob,
             x = total_hard_coral)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = detritivore),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  scale_y_continuous(name = "Detritivore abundance",
                     limits = c(0,40),
                     breaks = seq(0,40,by = 10)) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  ggtitle("P = 0.51")
```

# SCRAPERS

## summary table

```{r}
scra_mod_v2 |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict ta change

```{r}
scra_ta_pred <- scra_mod_v2 |> 
  emmeans(~ turf_algae, 
          at = ta_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## scra-ta plot

```{r}
f4_p9 <-
scra_ta_pred |> 
  ggplot(aes(y = prob,
             x = turf_algae)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = scraper),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("P = 0.80") +
  scale_y_continuous(limits = c(0,40),
                     breaks = seq(0,40,by = 10))
```

## predict ma change

```{r}
scra_ma_pred <- scra_mod_v2   |> 
  emmeans(~ total_macroalgae, 
          at = ma_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## scra-ma plot

```{r}
f4_p8 <- 
scra_ma_pred |> 
  ggplot(aes(y = prob,
             x = total_macroalgae)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = scraper),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ggtitle("P = 0.89") +
  scale_y_continuous(limits = c(0,40),
                     breaks = seq(0,40,by = 10))
```

## predict hc change

```{r}
scra_hc_pred <- scra_mod_v2  |> 
  emmeans(~ total_hard_coral, 
          at = hc_ab_newdata, 
          type = "response") |> 
  as.data.frame()

#herb_ta_pred |> head()
```

## scra-hc plot

```{r}
f4_p7 <-
scra_hc_pred |> 
  ggplot(aes(y = prob,
             x = total_hard_coral)) +
   geom_point(data = brt_bc_fishab_v3,
             aes(y = scraper),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2,
            color = "#DDD487") +
  geom_ribbon(aes(ymin = lower.HPD,
                  ymax = upper.HPD),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  scale_y_continuous(name = "Scraper abundance",
                     limits = c(0,40),
                     breaks = seq(0,40,by = 10)) +
  scale_x_continuous(name = "Percentage cover") +
  theme_classic() +
  ggtitle("P = 0.98")
```

# COMBINE PLOTS

```{r}
p_fg_abundance <-
(f4_p1 + f4_p2 + f4_p3) /
  (f4_p4 + f4_p5 + f4_p6) /
  (f4_p7 + f4_p8 + f4_p9)
```

## ggsave

```{r}
ggsave("Fig. 4. bc_fg_abundance.jpeg",
       plot = p_fg_abundance, 
       dpi = 600, 
       height = 7.5, 
       width = 7.5, 
       units = "in")
```

