---
title: "Data_prep"
format: html
editor: visual
---

# Clean up

```{r}
rm(list=ls())
gc()
```

# Description

This quarto documents contains database preparation involving the cleaning and combining of fish and benthic databases. Masterfile files are not provided as other colleagues are working on other aspects of the data

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
#source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# Read csv

## Load benthic csv

```{r}
benthic_master <- read_csv("Data/ROV_Relief_Slope_UPDATED.csv",
                           trim_ws = TRUE)

#glimpse(benthic_master)
```

### Find site names

Site names in the benthic file will dictate what sites to include in the fish file. This is because I needed to match the benthic and fish surveys. 

#### Database preparation (benthic)

##### Declare sites as factors

```{r}
benthic_master <- 
  benthic_master |> 
  mutate(Site = factor(Site),
         Survey = factor(Survey))
```

##### Check unique names for sites

```{r}
benthic_sites <-
benthic_master |> 
  with(unique(Site)) |> 
  as.tibble() |> 
  rename(Benthic_site_names = value)
```

##### Check unique names for surveys

```{r}
benthic_surveys <-
benthic_master |> 
  with(unique(Survey)) |> 
  as.tibble() |> 
  rename(Benthic_survey = value)
```

## Load fish csv

```{r}
fish_master <- read_csv("Data/master_ROV_fish_Tim_2.csv",
                        trim_ws = TRUE)

#glimpse(fish_master)
```

#### Database preparation (fish)

##### Declare sites as factors

```{r}
fish_master <-
  fish_master |> 
  mutate(Site = factor(Site),
         Reef_1 = factor(Reef_1),
         Reef_2 = factor(Reef_2))
```

##### Unique for surveys

```{r}
fish_survey <-
fish_master |> 
  with(unique(Survey)) |> 
  as.tibble() |> 
  rename(Fish_survey = value)
```

Filter survey data Feb_21, Jul_21, Feb_22

Filter only these dates as these dates had benthic surveys. 

##### Filter survey dates

```{r}
fish_master_v2 <- 
  fish_master |> 
  filter(Survey == "Feb_21" |
           Survey == "Jul_21" |
           Survey == "Feb_22")
```

##### Unique for sites

```{r}
fish_sites <-
fish_master_v2 |> 
  with(unique(Site)) |> 
  as.tibble() |> 
  rename(Fish_site_names = value)
```

## Benthic database

## Filter out problematic sites and then rename benthic sites

This was done to match fish database

```{r}
benthic_master_v2 <-
  benthic_master |> 
  mutate(Site_recode = recode(Site,
                       BVille_1 = "BOUG-01",
                       Chilcott_1 = "CHIL-01",
                       Edna_1 = "EDNA-01",
                       Edna_2 = "EDNA-01",
                       Edna_3 = "EDNA-01",
                       Flinders_N1 = "FLIN-02",
                       Flinders_S1 = "FLIN-01",
                       Fred_W1 = "FRED-01",
                       Herald_1 = "HERA-01",
                       HerSurp_1 = "HSUP-01",
                       Holmes_2 = "HOLM-02",
                       Juliette_1 = "JULI-01",
                       Juliette_2 = "JULI-02",
                       Lihou_N1 = "LORN-01",
                       Lihou_S1 = "HERM-01",
                       Lihou_S2 = "HERM-01",
                       Kenn_1 = "KENN-01",
                       Marion_1 = "MARI-01",
                       Osp_N1 = "OSPR-01",
                       Saumarez_S1 = "SAUM-01",
                       Willis_N1 = "WILL-01",
                       Wreck_E1 = "WREC-01")) |> 
  mutate(Survey_recode = recode(Survey,
                                "Feb-21" = "Feb_21",
                                "Jul-21" = "Jul_21",
                                "Feb-22" = "Feb_22"))
```

### Check levels of site in benthic database after changing the names

```{r}
benthic_master_v2 |> 
  with(unique(Site_recode)) |> 
  as.tibble() |> 
  arrange(value)
```

Looks correct

### Create new T_ID and filter relevant columns; make another column for total macroalgae and hard coral

```{r}
benthic_master_v3 <- 
benthic_master_v2 |> 
  mutate(New_ID = factor(paste(Survey_recode,
                               Site_recode,
                               Transect,
                               Depth,
                               sep = "|"))) |> 
  select(turf_algae: unconsolidated_subs,
         Transect,
         Depth,
         Survey:New_ID) |> 
  mutate(total_macroalgae = halimeda + macroalgae,
         total_hard_coral = HC_complex + HC_encrusting + HC_plate + HC_other + HC_massive_submass)
```

## Fish database

```{r}
fish_master_v3 <- 
fish_master_v2 |> 
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae") |> 
  pivot_wider(names_from = Functional.Group, # have functional group as columns so that all transects have values
              values_from = Number,
              values_fn = sum) |>  
  select(Survey, # select relevant columns
         Site,
         Transect,
         Depth_m,
         Benthic_Complexity,
         Habitat,
         `cropper/grazer`,
         browser,
         detritivore,
         excavator,
         scraper) |> 
  rename(cropper = `cropper/grazer`) |> 
  mutate(across(cropper: scraper,
         ~replace_na(.x, 0))) |> 
  filter(Site == "BOUG-01" | 
           Site == "CHIL-01" |
           Site == "EDNA-01" |
           Site == "FLIN-02" |
           Site == "FLIN-01" |
           Site == "FRED-01" |
           Site == "HERA-01" |
           Site == "HSUP-01" |
           Site == "HOLM-02" |
           Site == "JULI-01" |
           Site == "JULI-02" |
           Site == "HERM-01" |
           Site == "KENN-01" |
           Site == "MARI-01" |
           Site == "OSPR-01" |
           Site == "SAUM-01" |
           Site == "WILL-01" |
           Site == "WREC-01") |> 
  group_by(Survey,
           Site,
           Transect,
           Depth_m,
           Benthic_Complexity,
           Habitat) |> 
  summarise_at(vars(cropper:scraper),
               sum)
```


### Create new ID fish and filter only herbivore functional groups

'New ID' will be used to match the two databases

```{r}
fish_master_abun <-
  fish_master_v3 |> 
  mutate(New_ID = factor(paste(Survey,
                               Site,
                               Transect,
                               Depth_m,
                               sep = "|")))
```

# Data merging

## Merge fish abundance and benthic cover db

NAs are dropped

```{r}
fish_benthic_master <- 
fish_master_abun |> left_join(benthic_master_v3,
                               by = join_by(New_ID)) |> 
  drop_na()
```

### Export csv (fish abundance and benthic cover)

```{r}
db_fish_benthic <- write.csv(fish_benthic_master, "relationship_fish_ab_ben_version3.csv")
```

#### Checks: count number of sites

```{r}
fish_benthic_master |> 
  group_by(Site) |> 
  dplyr::summarise(Count = length(Site)) |> 
  ungroup()
```

### Export csv (benthic cover)

```{r}
db_benthic <- write.csv(benthic_master_v3, "db_benthic.csv")
```

# SPECIES RICHNESS

## all transects

```{r}
all_transects <- fish_master_v2 |> 
  mutate(New_ID = factor(paste(Survey, Site, Transect, Depth_m, sep = "|"))) |> 
  distinct(New_ID, Survey, Site, Transect, Depth_m, Benthic_Complexity, Habitat)
```

## sprich prep

```{r}
fish_sprich <-
fish_master_v2 |> 
  mutate(New_ID = factor(paste(Survey,
                               Site,
                               Transect,
                               Depth_m,
                               sep = "|"))) |> 
  filter(Functional.Group == "browser" |
           Functional.Group == "cropper/grazer" |
           Functional.Group == "detritivore" |
           Functional.Group == "excavator" |
           Functional.Group == "scraper") |> 
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae")
```

## Count number of species (species richness calcs)

```{r}
sp_count <- 
  fish_sprich |> 
  group_by(New_ID,
           Binomial) |> 
  dplyr::summarise(Count = sum(Number)) |> 
  ungroup()
```

## Long to wide format

```{r}
sp_count_wide <- 
sp_count |> 
  pivot_wider(names_from = Binomial,
              values_from = Count,
              values_fill = 0) 
```

## Remove column names cause iNEXT wont run with categorical variables in the matrix

```{r}
sp_count_wide_v2 <-
sp_count_wide |> 
  column_to_rownames("New_ID") |> 
  t() # transpose to make site columns and species rows

#View(sp_count_wide_v2)
```

### Run iNEXT

```{r}
sprich_inext <- sp_count_wide_v2 |> 
  iNEXT(q = c(0, 1),
        datatype = "abundance",
        endpoint = 1000,
        nboot = 100)

#sprich_inext$AsyEst
```

## Separate species richness estimates only

iNEXT returns other diversity metrics (eg Shannon-Weiner)

```{r}
spr_asym <- sprich_inext$AsyEst |> 
  filter(Diversity == "Species richness")
```

### Rename Assemblage into New_ID

```{r}
spr_asym <-
  spr_asym |> 
  rename(New_ID = Assemblage)
```

### Add transects that were filtered out because of 0 herbivores

```{r}
spr_asym_full <-
  all_transects |>
  left_join(spr_asym, by = "New_ID") |>
  mutate(
    Observed = replace_na(Observed, 0),
    Estimator = replace_na(Estimator, 0),
    s.e. = replace_na(s.e., 0),
    LCL = replace_na(LCL, 0),
    UCL = replace_na(UCL, 0)
  )
```

## Merge species richness and benthic cover

```{r}
fish_benthic_sp_master <-
spr_asym_full |> left_join(benthic_master_v3,
                               by = join_by(New_ID)) |> 
  drop_na()
```

### Add benthic complexity to the fish abundance and sprich database

```{r}
fish_master_v3_bc <- 
  all_transects |> 
  group_by(New_ID) |> 
  summarise(
    median_complexity = median(Benthic_Complexity, na.rm = TRUE),
    .groups = "drop"
  )

fish_benthic_sp_master <-
  fish_benthic_sp_master |> 
  left_join(fish_master_v3_bc, by = "New_ID")
```

### Export csv (fish richness and benthic cover)

```{r}
db_fishsp_benthic <- write.csv(fish_benthic_sp_master,
                                "relationship_fish_sp_ben_v2.csv") # use this database
```
