---
title: "Data_prep"
format: html
editor: visual
---

# load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
#source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# read csv

## benthic file

```{r}
benthic_master <- read_csv("Data/ROV_Relief_Slope_UPDATED.csv",
                           trim_ws = TRUE)

glimpse(benthic_master)
```

### find site names

-   Site names in the benthic file will dictate what sites to include in the fish file

declare site as factor

```{r}
benthic_master <- 
  benthic_master |> 
  mutate(Site = factor(Site),
         Survey = factor(Survey))
```

check levels of site

```{r}
benthic_sites <-
benthic_master |> 
  with(unique(Site)) |> 
  as.tibble() |> 
  rename(Benthic_site_names = value)
```

unique for survey

```{r}
benthic_surveys <-
benthic_master |> 
  with(unique(Survey)) |> 
  as.tibble() |> 
  rename(Benthic_survey = value)
```

## fish file

```{r}
fish_master <- read_csv("Data/master_ROV_fish_Tim_2.csv",
                        trim_ws = TRUE)

#glimpse(fish_master)
```

declare site as factors

```{r}
fish_master <-
  fish_master |> 
  mutate(Site = factor(Site),
         Reef_1 = factor(Reef_1),
         Reef_2 = factor(Reef_2))
```

### check levels of survey

```{r}
fish_survey <-
fish_master |> 
  with(unique(Survey)) |> 
  as.tibble() |> 
  rename(Fish_survey = value)
```

-   filter survey datas Feb_21, Jul_21, Feb_22

-   filter only these dates as these dates had benthic surveys

```{r}
fish_master_v2 <- 
  fish_master |> 
  filter(Survey == "Feb_21" |
           Survey == "Jul_21" |
           Survey == "Feb_22")
```

### check levels of site

```{r}
fish_sites <-
fish_master_v2 |> 
  with(unique(Site)) |> 
  as.tibble() |> 
  rename(Fish_site_names = value)
```

# check site names manually

-   problematic sites in benthic_master
    -   Lihou_N1,
    -   Lihou_S1,
    -   Lihou_S2

```{r}
benthic_master |> 
  filter(Site == "Edna_3")
```

names for Lihou

```{r}
fish_master_v2 |> 
  filter(Reef_1 == "Lihou") |> 
  with(unique(Reef_2))
```

```{r}
fish_master_v2 |> 
  filter(Site == "CHIL-01") 
```

# BENTHIC DATABASE

## filter out problematic sites and then rename the benthic site names

```{r}
benthic_master_v2 <-
  benthic_master |> 
  mutate(Site_recode = recode(Site,
                       BVille_1 = "BOUG-01",
                       Chilcott_1 = "CHIL-01",
                       Edna_1 = "EDNA-01",
                       Edna_2 = "EDNA-01",
                       Edna_3 = "EDNA-01",
                       Flinders_N1 = "FLIN-02",
                       Flinders_S1 = "FLIN-01",
                       Fred_W1 = "FRED-01",
                       Herald_1 = "HERA-01",
                       HerSurp_1 = "HSUP-01",
                       Holmes_2 = "HOLM-02",
                       Juliette_1 = "JULI-01",
                       Juliette_2 = "JULI-02",
                       Lihou_N1 = "LORN-01",
                       Lihou_S1 = "HERM-01",
                       Lihou_S2 = "HERM-01",
                       Kenn_1 = "KENN-01",
                       Marion_1 = "MARI-01",
                       Osp_N1 = "OSPR-01",
                       Saumarez_S1 = "SAUM-01",
                       Willis_N1 = "WILL-01",
                       Wreck_E1 = "WREC-01")) |> 
  mutate(Survey_recode = recode(Survey,
                                "Feb-21" = "Feb_21",
                                "Jul-21" = "Jul_21",
                                "Feb-22" = "Feb_22"))
```

```{r}
benthic_master_v2 |> 
  filter(Site_recode == "HERM-01")
```


### check levels of site in benthic database after changing the names

-   looks correct

```{r}
benthic_master_v2 |> 
  with(unique(Site_recode)) |> 
  as.tibble() |> 
  arrange(value)
```

## create new T_ID and filter relevant columns; make another column for total macroalgae and hard coral

```{r}
benthic_master_v3 <- 
benthic_master_v2 |> 
  mutate(New_ID = factor(paste(Survey_recode,
                               Site_recode,
                               Transect,
                               Depth,
                               sep = "|"))) |> 
  select(turf_algae: unconsolidated_subs,
         Transect,
         Depth,
         Survey:New_ID) |> 
  mutate(total_macroalgae = halimeda + macroalgae,
         total_hard_coral = HC_complex + HC_encrusting + HC_plate + HC_other + HC_massive_submass)
```

# FISH DATABASE

## New ID fish and filter only herbivore functional groups

```{r}
fish_master_v3 <-
fish_master_v2 |> 
  mutate(New_ID = factor(paste(Survey,
                               Site,
                               Transect,
                               Depth_m,
                               sep = "|"))) |> 
  filter(Functional.Group == "browser" |
           Functional.Group == "cropper/grazer" |
           Functional.Group == "detritivore" |
           Functional.Group == "excavator" |
           Functional.Group == "scraper") |> 
  filter(Family != "Chanidae" & # remove families mislabelled as herbivores
           Family != "Ostraciidae" &
           Family != "Pomacentridae" &
           Family != "Tetraodontidae")
```

## wide format with functional groups as column names and values as abundance; filter relevant sites

```{r}
fish_master_abun <- 
fish_master_v3 |> 
  pivot_wider(names_from = Functional.Group, 
              values_from = Number,
              values_fn = sum) |> 
  select(New_ID,
         Site,
         Transect,
         Depth_m,
         Benthic_Complexity,
         `cropper/grazer`,
         browser,
         detritivore,
         excavator,
         scraper) |> 
  rename(cropper = `cropper/grazer`) |> 
  mutate(across(cropper: scraper,
         ~replace_na(.x, 0))) |> 
  filter(Site == "BOUG-01" | 
           Site == "CHIL-01" |
           Site == "EDNA-01" |
           Site == "FLIN-02" |
           Site == "FLIN-01" |
           Site == "FRED-01" |
           Site == "HERA-01" |
           Site == "HSUP-01" |
           Site == "HOLM-02" |
           Site == "JULI-01" |
           Site == "JULI-02" |
           Site == "HERM-01" |
           Site == "KENN-01" |
           Site == "MARI-01" |
           Site == "OSPR-01" |
           Site == "SAUM-01" |
           Site == "WILL-01" |
           Site == "WREC-01") |> 
  group_by(New_ID,
           Site,
           Transect,
           Depth_m,
           Benthic_Complexity) |> 
  summarise_at(vars(cropper:scraper),
               sum)
```


```{r}
fish_master_abun |>
  filter(Site == "HERM-01") 
```


# DATA MERGING (benthic and fish abundance)

```{r}
benthic_fish_master <- 
benthic_master_v3 |> left_join(fish_master_abun,
                               by = join_by(New_ID)) |> 
  drop_na()
```

-   51 transects with NAs

# export csv (benthic_fish_database)

```{r}
db_benthic_fish <- write.csv(benthic_fish_master, "relationship_ben_fish_ab.csv") # dont use this
```

# checking

```{r}
fish_master_abun |> 
  filter(Site == "HERA-01")
```

# JOIN ABUNDANCE AND BENTHIC COVER

```{r}
fish_benthic_master <- 
fish_master_abun |> left_join(benthic_master_v3,
                               by = join_by(New_ID)) |> 
  drop_na()
```

# export csv (fish_benthic_database)

```{r}
db_fish_benthic <- write.csv(fish_benthic_master, "relationship_fish_ab_ben_version2.csv") # use this database
```

-   38 NAs

# count number of sites

```{r}
fish_benthic_master |> 
  group_by(Site) |> 
  dplyr::summarise(Count = length(Site)) |> 
  ungroup()
```


# export csv (benthic cover)

```{r}
db_benthic <- write.csv(benthic_master_v3, "db_benthic.csv")
```

## wide format with functional groups as column names and values as biomass; filter relevant sites

```{r}
fish_master_biom <- 
fish_master_v3 |> 
  mutate(Biomass_KG = Biomass_G / 1000) |> 
  pivot_wider(names_from = Functional.Group, 
              values_from = Biomass_KG,
              values_fn = sum) |> 
  select(New_ID,
         Site,
         Transect,
         Depth_m,
         Benthic_Complexity,
         `cropper/grazer`,
         browser,
         detritivore,
         excavator,
         scraper) |> 
  rename(cropper = `cropper/grazer`) |> 
  mutate(across(cropper: scraper,
         ~replace_na(.x, 0))) |> 
  filter(Site == "BOUG-01" | 
           Site == "CHIL-01" |
           Site == "EDNA-01" |
           Site == "FLIN-02" |
           Site == "FLIN-01" |
           Site == "FRED-01" |
           Site == "HERA-01" |
           Site == "HSUP-01" |
           Site == "HOLM-02" |
           Site == "JULI-01" |
           Site == "JULI-02" |
           Site == "HERM-01" |
           Site == "KENN-01" |
           Site == "MARI-01" |
           Site == "OSPR-01" |
           Site == "SAUM-01" |
           Site == "WILL-01" |
           Site == "WREC-01") |> 
  group_by(New_ID,
           Site,
           Transect,
           Depth_m,
           Benthic_Complexity) |> 
  summarise_at(vars(cropper:scraper),
               sum)
```

# JOIN BIOMASS AND BENTHIC COVER

```{r}
fish_benthic_bio_master <- 
fish_master_biom |> left_join(benthic_master_v3,
                               by = join_by(New_ID)) |> 
  drop_na()
```

# export csv (fish_benthic_database)

```{r}
db_fishbio_benthic <- write.csv(fish_benthic_bio_master,
                                "relationship_fish_bio_ben.csv") # use this database
```

# count number of sites

```{r}

```


# SPECIES RICHNESS

## count number of species

```{r}
sp_count <- 
  fish_master_v3 |> 
  group_by(New_ID,
           Binomial) |> 
  dplyr::summarise(Count = sum(Number)) |> 
  ungroup()
```

## long to wide format

```{r}
sp_count_wide <- 
sp_count |> 
  pivot_wider(names_from = Binomial,
              values_from = Count,
              values_fill = 0) 
```

## Remove column names cause iNEXT wont run with categorical

```{r}
sp_count_wide_v2 <-
sp_count_wide |> 
  column_to_rownames("New_ID") |> 
  t() # transpose to make site columns and species rows

View(sp_count_wide_v2)
```

### run iNEXT

```{r}
sprich_inext <- sp_count_wide_v2 |> 
  iNEXT(q = c(0, 1),
        datatype = "abundance",
        endpoint = 1000,
        nboot = 100)

#sprich_inext$AsyEst
```

### Separate species richness only

```{r}
spr_asym <- sprich_inext$AsyEst |> 
  filter(Diversity == "Species richness")
```
### rename Assemblage into New_ID

```{r}
spr_asym <-
  spr_asym |> 
  rename(New_ID = Assemblage)
```
## JOIN SP RICH AND BENTHIC COVER

```{r}
fish_benthic_sp_master <-
spr_asym |> left_join(benthic_master_v3,
                               by = join_by(New_ID)) |> 
  drop_na()
```

## export csv (fish_benthic_database)

```{r}
db_fishsp_benthic <- write.csv(fish_benthic_sp_master,
                                "relationship_fish_sp_ben.csv") # use this database
```
