---
title: "Benthic_fits"
format: html
editor: visual
---

```{r}
rm(list=ls())
gc()
```

# Description

This quarto document contains GAMM analysis to examine changes in benthic cover with depth.

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# Variables of interest

-   total_hard_coral
-   total_macroalgae
-   turf_algae
-   total_octocoral
-   rock
-   unconsolidated_subs

# Upload csv

```{r}
benthic <- read_csv("Data/db_benthic.csv", trim_ws = TRUE)
```

# Prepare db

```{r}
benthic_v2 <- 
  benthic |>
  mutate(Site_recode = factor(Site_recode),
         total_octocoral = complex_octocoral + other_octocoral) |> 
  select(Depth,
         Site_recode,
         Habitat,
         Aspect_descriptive,
         total_hard_coral,
         total_macroalgae,
         total_octocoral,
         turf_algae,
         sponge,
         unconsolidated_subs) |> 
  mutate(prop_hc = total_hard_coral / 100,
         prop_ma = total_macroalgae / 100,
         prop_oct = total_octocoral / 100,
         prop_ta = turf_algae / 100,
         prop_sponge = sponge / 100,
         prop_us = unconsolidated_subs / 100) |> 
  filter(Habitat == "outer_reef")

#glimpse(benthic_v2)
```

# Coral model

## Def formula

```{r}
coral_form <- bf(prop_hc ~ s(Depth,
                             bs = "cr",
                             k = 3) +
                   (1 | Site_recode) +
                   (1 | Habitat) +
                   (1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```

## Get priors

```{r}
get_prior(coral_form, data = benthic_v2)
```

Priors needed

b, Intercept, phi, sd, sds, zi

## Def prior

```{r}
coral_prior <- prior(normal(2.2, 1.7), class = "Intercept") +
  prior(normal(0, 20), class = "b") +
  prior(student_t(3, 0 , 20), class = "sds") +
  prior(student_t(3, 0, 1.7), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
coral_mod <- brms::brm(coral_form,
                data = benthic_v2,
                prior = coral_prior,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

# Save HC mod

```{r}
save(coral_mod, file = "Model_Ouput/coral_mod.Rdata")
```

### Conditional effects

```{r}
coral_mod |> conditional_effects() |> plot() 
```

### MCMC diagnostics

```{r}
coral_mod |> mcmc_plot(type = "trace")
coral_mod |> mcmc_plot(type = "acf_bar")
coral_mod |> mcmc_plot(type = "rhat_hist")
coral_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
coral_resids <- make_brms_dharma_res(coral_mod)

coral_resids |> testUniformity()
coral_resids |> plotResiduals(quantreg = FALSE)
```

# Macroalgae model

## Def formula

```{r}
ma_form <- bf(prop_ma ~ s(Depth,
                          bs = "cr",
                          k = 3) +
                    (1 | Site_recode) +
                   (1 | Habitat) +
                   (1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```


## Def prior

```{r}
ma_prior <- prior(normal(1.8, 1.4), class = "Intercept") +
  prior(normal(0, 15), class = "b") +
  prior(student_t(3, 0 , 15), class = "sds") +
  prior(student_t(3, 0, 1.4), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
ma_mod <- brm(ma_form,
                data = benthic_v2,
                prior = ma_prior,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

## Save MA model

```{r}
save(ma_mod, file = "Model_Ouput/ma_mod.Rdata")
```

### Conditional effects

```{r}
ma_mod |> conditional_effects() |> plot() 
```

### MCMC diagnostics

```{r}
ma_mod |> mcmc_plot(type = "trace")
ma_mod |> mcmc_plot(type = "acf_bar")
ma_mod |> mcmc_plot(type = "rhat_hist")
ma_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
ma_resids <- make_brms_dharma_res(ma_mod)

ma_resids |> testUniformity()
ma_resids |> plotResiduals(quantreg = FALSE)
```

# TURFS

## Def formula

```{r}
ta_form <- bf(prop_ta ~ s(Depth,
                          bs = "cr",
                          k = 3) +
                   (1 | Site_recode) +
                   (1 | Habitat) +
                   (1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```


## Def prior

```{r}
ta_prior <- prior(normal(2.6, 2.2), class = "Intercept") +
  prior(normal(0, 22), class = "b") +
  prior(student_t(3, 0 , 22), class = "sds") +
  prior(student_t(3, 0, 2.2), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
ta_mod <- brm(ta_form,
                data = benthic_v2,
                prior = ta_prior,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

## Save TA model

```{r}
save(ta_mod, file = "Data/ta_mod.Rdata")
```

### Conditional effects

```{r}
ta_mod |> conditional_effects() |> plot(points = TRUE) 
```

### MCMC diagnostics

```{r}
ta_mod |> mcmc_plot(type = "trace")
ta_mod |> mcmc_plot(type = "acf_bar")
ta_mod |> mcmc_plot(type = "rhat_hist")
ta_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
ta_resids <- make_brms_dharma_res(ta_mod)

ta_resids |> testUniformity()
ta_resids |> plotResiduals(quantreg = FALSE)
```

# OCTOCORAL

## Def formula

```{r}
oct_form <- bf(prop_oct ~ s(Depth,
                            bs = "cr",
                            k = 3) +
                   (1 | Site_recode), #+
                   #(1 | Habitat) +
                   #(1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```


## Def prior

```{r}
oct_prior <- prior(normal(2.5, 2), class = "Intercept") +
  prior(normal(0, 20), class = "b") +
  prior(student_t(3, 0 , 20), class = "sds") +
  prior(student_t(3, 0, 2), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
oct_mod <- brm(oct_form,
                data = benthic_v2,
                prior = oct_prior,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

## Save oct model

```{r}
save(oct_mod, file = "Model_Output/oct_mod.Rdata")
```

### Conditional effects

```{r}
oct_mod |> conditional_effects() |> plot(points = TRUE) 
```

### MCMC diagnostics

```{r}
oct_mod |> mcmc_plot(type = "trace")
oct_mod |> mcmc_plot(type = "acf_bar")
oct_mod |> mcmc_plot(type = "rhat_hist")
oct_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
oct_resids <- make_brms_dharma_res(oct_mod)

oct_resids |> testUniformity()
oct_resids |> plotResiduals(quantreg = FALSE)
```

# UNCONSOLIDATED SUBSTRATE

## Def formula

```{r}
us_form <- bf(prop_us ~ s(Depth,
                          bs = "cr",
                          k = 3) +
                   (1 | Site_recode) +
                   (1 | Habitat) +
                   (1 | Aspect_descriptive),
                 family = zero_one_inflated_beta())
```

## Get prior

```{r}
get_prior(us_form, data = benthic_v2)
```

## Def prior

```{r}
us_prior <- prior(normal(1.9, 1.4), class = "Intercept") +
  prior(normal(0, 14), class = "b") +
  prior(student_t(3, 0 , 14), class = "sds") +
  prior(student_t(3, 0, 1.4), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1, 1), class = "coi") +
  prior(beta(1, 1), class = "zoi")
```

## Fit full model

```{r}
#| cache: TRUE
us_mod <- brm(us_form,
                data = benthic_v2,
                prior = us_prior,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

## Save us model

```{r}
save(us_mod, file = "Model_Output/us_mod.Rdata")
```

### Conditional effects

```{r}
us_mod |> conditional_effects() |> plot() 
```

### MCMC diagnostics

```{r}
us_mod |> mcmc_plot(type = "trace")
us_mod |> mcmc_plot(type = "acf_bar")
us_mod |> mcmc_plot(type = "rhat_hist")
us_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
us_resids <- make_brms_dharma_res(us_mod)

us_resids |> testUniformity()
us_resids |> plotResiduals(quantreg = FALSE)
```

# SPONGE

## Def formula

```{r}
sp_form <- bf(prop_sponge ~ s(Depth,
                            bs = "cr",
                            k = 3) +
                   (1 | Site_recode) +
                   (1 | Habitat) +
                   (1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```


## Def prior

```{r}
sp_prior <- prior(normal(4.2, 3.8), class = "Intercept") + 
  prior(normal(0, 1.1), class = "b") + # still need to optimize this
  prior(student_t(3, 0, 1.1), class = "sds") +
  prior(student_t(3, 0, 3.8), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit model

```{r}
#| cache: TRUE
sp_mod <- brm(sp_form,
                data = benthic_v2,
                prior = sp_prior,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

## Save model

```{r}
save(sp_mod, file = "Model_Output/sp_mod.Rdata")
```

### Conditional effects

```{r}
sp_mod |> conditional_effects() |> plot() 
```

### MCMC diagnostics

```{r}
sp_mod |> mcmc_plot(type = "trace")
sp_mod |> mcmc_plot(type = "acf_bar")
sp_mod|> mcmc_plot(type = "rhat_hist")
sp_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
sp_resids <- make_brms_dharma_res(sp_mod)

sp_resids |> testUniformity()
sp_resids |> plotResiduals(quantreg = FALSE)
```

# ROCK

## Def formula

```{r}
rock_form <- bf(prop_rock ~ s(Depth) +
                   (1 | Site_recode),
                 family = zero_inflated_beta())
```


## Def prior

```{r}
rock_prior <- prior(normal(3, 2.5), class = "Intercept") +
  prior(normal(0, 1.2), class = "b") +
  prior(student_t(3, 0 , 2.5), class = "sds") +
  prior(student_t(3, 0, 2.5), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
rock_mod <- brm(rock_form,
                data = benthic_v2,
                prior = rock_prior,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 0)
```

### MCMC diagnostics

```{r}
rock_mod |> mcmc_plot(type = "trace")
rock_mod |> mcmc_plot(type = "acf_bar")
rock_mod |> mcmc_plot(type = "rhat_hist")
rock_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
rock_resids <- make_brms_dharma_res(rock_mod)

rock_resids |> testUniformity()
rock_resids |> plotResiduals(quantreg = FALSE)
```
