---
title: "benthic_model_fits_glmms"
format: html
editor: visual
---

# Cleanup

```{r}
rm(list=ls())
gc()
```

# Description

Contains GLMM to examine changes in benthic cover with depth. LOO comparisons between GLMM and GAMM (in another quarto document) were conducted to determine which model best represented changes in cover with depth.

# Library

```{r}
# load library
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
set.seed(123)
```

# Load csv

```{r}
benthic <- read_csv("Data/db_benthic.csv", trim_ws = TRUE)
```

## EDA: Plotting coral morphology and depth

```{r}
benthic |>  
  select(HC_complex, HC_encrusting, HC_plate, HC_massive_submass, Depth) |> 
  pivot_longer(cols = c(HC_complex, HC_encrusting, HC_plate, HC_massive_submass),
               names_to = "Morphology",
               values_to = "Cover") |> 
  ggplot(aes(x = Depth, y = Cover)) +
  facet_wrap(~Morphology, scales = "free") +
  geom_point() +
  geom_smooth(method = "loess")
```

## EDA: determine number of distint transects and sites

```{r}
benthic |> 
   filter(Habitat == "outer_reef") |> 
  #group_by(Site_recode) |> 
  summarise(nTransect = n_distinct(Transect))

benthic |> 
   filter(Habitat == "outer_reef") |> 
  #group_by(Site_recode) |> 
  summarise(nSite = n_distinct(Site_recode))

benthic |> 
   filter(Habitat == "outer_reef") |> 
  #group_by(Site_recode) |> 
  distinct(Site_recode)
```

# Prepare db

```{r}
benthic_v2 <- 
  benthic |>
  mutate(Site_recode = factor(Site_recode),
         total_octocoral = complex_octocoral + other_octocoral) |> 
  select(Depth,
         Site_recode,
         Habitat,
         Aspect_descriptive,
         total_hard_coral,
         total_macroalgae,
         total_octocoral,
         turf_algae,
         sponge,
         unconsolidated_subs) |> 
  mutate(prop_hc = total_hard_coral / 100,
         prop_ma = total_macroalgae / 100,
         prop_oct = total_octocoral / 100,
         prop_ta = turf_algae / 100,
         prop_sponge = sponge / 100,
         prop_us = unconsolidated_subs / 100) |> 
  filter(Habitat == "outer_reef")
```

# CORAL

## Def formula

```{r}
coral_form_glm <- bf(prop_hc ~ Depth +
                   (1 | Site_recode), 
                  # (1 | Habitat) +
                  # (1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```

## Get prior

```{r}
get_prior(coral_form_glm, data = benthic_v2)
```

## Def prior

```{r}
coral_prior_glm <- prior(normal(2.2, 1.7), class = "Intercept") +
  prior(normal(0, 1.3), class = "b") +
  #prior(student_t(3, 0 , 1.7), class = "sds") +
  prior(student_t(3, 0, 1.7), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
coral_mod_glm <- brm(coral_form_glm,
                data = benthic_v2,
                prior = coral_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                seed = 123,
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

### MCMC diagnostics

```{r}
coral_mod_glm |> mcmc_plot(type = "trace")
coral_mod_glm |> mcmc_plot(type = "acf_bar")
coral_mod_glm |> mcmc_plot(type = "rhat_hist")
coral_mod_glm |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
coral_resids_glm <- make_brms_dharma_res(coral_mod_glm)

# qqplot
coral_resids_glm |> testUniformity()
coral_resids_glm |> plotResiduals(quantreg = FALSE)
```

### Save model

```{r}
save(coral_mod_glm, file = "Model_Output/coral_mod_glm.Rdata")
```

# MACROALGAE

## Def formula

```{r}
ma_form_glm <- bf(prop_ma ~ Depth +
                   (1 | Site_recode),  
                    #(1 | Habitat) +
                   #(1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```

## Def prior

```{r}
ma_prior_glm <- prior(normal(1.8, 1.4), class = "Intercept") +
  prior(normal(0, 1.3), class = "b") +
  #prior(student_t(3, 0 , 1.4), class = "sds") +
  prior(student_t(3, 0, 1.4), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
ma_mod_glm <- brm(ma_form_glm,
                data = benthic_v2,
                prior = ma_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 0)
```

### MCMC diagnostics

```{r}
ma_mod_glm |> mcmc_plot(type = "trace")
ma_mod_glm |> mcmc_plot(type = "acf_bar")
ma_mod_glm |> mcmc_plot(type = "rhat_hist")
ma_mod_glm |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
ma_resids_glm <- make_brms_dharma_res(ma_mod_glm)

# qqplot
ma_resids_glm |> testUniformity()
ma_resids_glm |> plotResiduals(quantreg = FALSE)
```

### Save model

```{r}
save(ma_mod_glm, file = "Model_Output/ma_mod_glm.Rdata")
```

# TURFS

## Def formula

```{r}
ta_form_glm <- bf(prop_ta ~ Depth +
                   (1 | Site_recode), 
                    #(1 | Habitat) +
                   #(1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```

## Def prior

```{r}
ta_prior_glm <- prior(normal(2.6, 2.2), class = "Intercept") +
  prior(normal(0, 1.2), class = "b") +
  #prior(student_t(3, 0 , 2.2), class = "sds") +
  prior(student_t(3, 0, 2.2), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
ta_mod_glm <- brm(ta_form_glm,
                data = benthic_v2,
                prior = ta_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

### MCMC diagnostics

```{r}
ta_mod_glm |> mcmc_plot(type = "trace")
ta_mod_glm |> mcmc_plot(type = "acf_bar")
ta_mod_glm |> mcmc_plot(type = "rhat_hist")
ta_mod_glm |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
ta_resids_glm <- make_brms_dharma_res(ta_mod_glm)

# qqplot
ta_resids_glm |> testUniformity()
ta_resids_glm |> plotResiduals(quantreg = FALSE)
```

### Save model

```{r}
save(ta_mod_glm, file = "Model_Output/ta_mod_glm.Rdata")
```

# OCTOCORAL

## Def formula

```{r}
oct_form_glm <- bf(prop_oct ~ Depth + 
                     (1 | Site_recode) + 
                    (1 | Habitat) +
                   (1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```

## Def prior

```{r}
oct_prior_glm <- prior(normal(2.5, 2), class = "Intercept") +
  prior(normal(0, 1.2), class = "b") +
  #prior(student_t(3, 0 , 2), class = "sds") +
  prior(student_t(3, 0, 2), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
oct_mod_glm <- brm(oct_form_glm,
                data = benthic_v2,
                prior = oct_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

### MCMC diagnostics

```{r}
oct_mod_glm |> mcmc_plot(type = "trace")
oct_mod_glm |> mcmc_plot(type = "acf_bar")
oct_mod_glm |> mcmc_plot(type = "rhat_hist")
oct_mod_glm |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
oct_resids_glm <- make_brms_dharma_res(oct_mod_glm)

oct_resids_glm |> testUniformity()
oct_resids_glm |> plotResiduals(quantreg = FALSE)
```

## Save model

```{r}
save(oct_mod_glm, file = "Model_Output/oct_mod_glm.Rdata")
```

# UNCONSOLIDATED SUBSTRATE

## Def formula

```{r}
us_form_glm <- bf(prop_us ~ Depth +
                   (1 | Site_recode), #+ 
                    #(1 | Habitat) +
                   #(1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```

## Get prior

```{r}
get_prior(us_form_glm, data = benthic_v2)
```

## Def prior

```{r}
us_prior_glm <- prior(normal(1.9, 1.4), class = "Intercept") +
  prior(normal(0, 1.3), class = "b") +
  #prior(student_t(3, 0 , 1.4), class = "sds") +
  prior(student_t(3, 0, 1.4), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
 # prior(beta(1, 1), class = "coi") +
  prior(beta(1, 1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
us_mod_glm <- brm(us_form_glm,
                data = benthic_v2,
                prior = us_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

### MCMC diagnostics

```{r}
us_mod_glm |> mcmc_plot(type = "trace")
us_mod_glm |> mcmc_plot(type = "acf_bar")
us_mod_glm |> mcmc_plot(type = "rhat_hist")
us_mod_glm |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
us_resids_glm <- make_brms_dharma_res(us_mod_glm)

us_resids_glm |> testUniformity()
us_resids_glm |> plotResiduals(quantreg = FALSE)
```

## Save model

```{r}
save(us_mod_glm, file = "Model_Output/us_mod_glm.Rdata")
```

# SPONGE

## Def formula

```{r}
sp_form_glm <- bf(prop_sponge ~ Depth +
                   (1 | Site_recode),# + 
                    #(1 | Habitat) +
                   #(1 | Aspect_descriptive),
                 family = zero_inflated_beta())
```

## Get pripr

```{r}
get_prior(sp_form_glm, data = benthic_v2)
```

## Def prior

```{r}
sp_prior_glm <- prior(normal(4.2, 3.8), class = "Intercept") +
  prior(normal(0, 1.1), class = "b") +
  #prior(student_t(3, 0 , 1.4), class = "sds") +
  prior(student_t(3, 0, 1.1), class = "sd") +
  prior(gamma(0.01, 0.01), class = "phi") +
  prior(beta(1,1), class = "zi")
```

## Fit full model

```{r}
#| cache: TRUE
sp_mod_glm <- brm(sp_form_glm,
                data = benthic_v2,
                prior = sp_prior_glm,
                sample_prior = "yes",
                iter = 10000,
                warmup = 2000,
                chains = 3, 
                cores = 6,
                thin = 5, 
                control = list(adapt_delta = 0.99,
                                 max_treedepth = 20),
                refresh = 2000)
```

## Save model

```{r}
save(sp_mod_glm, file = "Model_Output/sp_mod_glm.Rdata")
```

### MCMC diagnostics

```{r}
sp_mod_glm |> mcmc_plot(type = "trace")
sp_mod_glm |> mcmc_plot(type = "acf_bar")
sp_mod_glm |> mcmc_plot(type = "rhat_hist")
sp_mod_glm |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
sp_resids_glm <- make_brms_dharma_res(sp_mod_glm)

# qqplot
sp_resids_glm |> testUniformity()
sp_resids_glm |> plotResiduals(quantreg = FALSE)
```

# LOO COMPARE

-Greater loo (elpd diff) is the best model

# CORAL

## Load models

```{r}
load("Model_Output/coral_mod.Rdata") # gam model
load("Model_Output/coral_mod_glm.Rdata")
```

### LOO

```{r}
loo_compare(brms::loo(coral_mod), # gam model
            brms::loo(coral_mod_glm)) 
```

# MACROALGAE

## Load models

```{r}
load("Data/ma_mod.Rdata") # gam model
load("Data/ma_mod_glm.Rdata")
```

### LOO

```{r}
loo_compare(brms::loo(ma_mod), # gam model
            brms::loo(ma_mod_glm)) 
```

# TURFS

## Load models

```{r}
load("Data/ta_mod.Rdata") # gam model
load("Data/ta_mod_glm.Rdata")
```

### LOO

```{r}
loo_compare(brms::loo(ta_mod), # gam model
            brms::loo(ta_mod_glm)) 
```

# OCTOCORAL

## Load models

```{r}
load("Data/oct_mod.Rdata") # gam model
load("Data/oct_mod_glm.Rdata")
```

### LOO

```{r}
loo_compare(brms::loo(oct_mod), # gam model
            brms::loo(oct_mod_glm)) 
```

# UNCONSOLIDATED SUBSTRATA

## Load models

```{r}
load("Data/us_mod.Rdata") # gam model
load("Data/us_mod_glm.Rdata")
```

### LOO

```{r}
loo_compare(brms::loo(us_mod), # gam model
            brms::loo(us_mod_glm)) 
```

# SPONGE

## Load models

```{r}
load("Data/sp_mod.Rdata") 
load("Data/sp_mod_glm.Rdata")
```

### LOO

```{r}
loo_compare(brms::loo(sp_mod), # gam model
            brms::loo(sp_mod_glm)) 
```
