---
title: "benthic_results_plots_version3"
format: html
editor: visual
---

# Cleanup

```{r}
rm(list=ls())
gc()
```

# Description

Code for plotting figures from the GLMM/GLMM posterior predictions.

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
```

# Load csv

```{r}
benthic <- read_csv("Data/db_benthic.csv", trim_ws = TRUE)
```

# Prepare db

```{r}
benthic_v2 <- 
  benthic |>
  mutate(Site_recode = factor(Site_recode),
         total_octocoral = complex_octocoral + other_octocoral) |> 
  select(Depth,
         Site_recode,
         Habitat,
         Aspect_descriptive,
         total_hard_coral,
         total_macroalgae,
         total_octocoral,
         turf_algae,
         sponge,
         unconsolidated_subs) |> 
  mutate(prop_hc = total_hard_coral / 100,
         prop_ma = total_macroalgae / 100,
         prop_oct = total_octocoral / 100,
         prop_ta = turf_algae / 100,
         prop_sponge = sponge / 100,
         prop_us = unconsolidated_subs / 100) |> 
  filter(Habitat == "outer_reef")

#glimpse(benthic_v2)
```

## Newdata

```{r}
depth_newdata <- with(benthic_v2,
                      data.frame(Depth = seq(min(Depth),
                                             max(Depth),
                                             length = 100)))
```

# CORAL

## Load model

```{r}
load("Model_Output/coral_mod_glm.Rdata")
```

## Summary table

```{r}
coral_mod_glm |> as_draws_df() |> 
  dplyr::select(matches("^b_.*|^bs.*|sds.*")) |>  
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## Emmeans

```{r}
coral_em <- 
  coral_mod_glm |> 
  emmeans(~ Depth,
          at = depth_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
coral_em_draws <- 
gather_emmeans_draws(coral_em)
```

## Subset 200 draws

```{r}
coral_draw_subset <- sample(unique(coral_em_draws$.draw), 200)

coral_em_draws_200 <- coral_em_draws  |>  
  filter(.draw %in% coral_draw_subset)
```

## Plot

```{r}
p3_hard_coral <- 
coral_em_draws_200 |> 
  ggplot(aes(x = Depth, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "Proportional cover",
                     limits = c(0,0.75),
                     breaks = seq(0, 0.75, by = 0.25)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  ggtitle("Hard coral") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# MACROALGAE

## Load model

```{r}
load("Model_Output/ma_mod_glm.Rdata")
```

## Summary table

```{r}
ma_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
  dplyr::select(matches("^b_.*|^bs.*|sds.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## Emmeans

```{r}
ma_em <- 
  ma_mod_glm |> 
  emmeans(~ Depth,
          at = depth_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
ma_em_draws <- 
gather_emmeans_draws(ma_em)
```

## Subset 200 draws

```{r}
ma_draw_subset <- sample(unique(ma_em_draws$.draw), 200)

ma_em_draws_200 <- ma_em_draws  |>  
  filter(.draw %in% ma_draw_subset)
```

## Plot

```{r}
p1_ma <- 
ma_em_draws_200 |> 
  ggplot(aes(x = Depth, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#8AA17D", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkgreen", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkgreen", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "Proportional cover",
                     limits = c(0,0.75),
                     breaks = seq(0, 0.75, by = 0.25)) +
  theme_classic() +
  scale_x_continuous(name = "Depth (m)") +
  ggtitle("Macroalgae") +
  theme_classic() +
  theme(axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        #axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# TURFS

## Load model

```{r}
load("Model_Output/ta_mod_glm.Rdata")
```

## Summary table

```{r}
ta_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
    dplyr::select(matches("^b_.*|^bs.*|sds.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## Emmeans

```{r}
ta_em <- 
  ta_mod_glm |> 
  emmeans(~ Depth,
          at = depth_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
ta_em_draws <- 
gather_emmeans_draws(ta_em)
```

## Subset 200 draws

```{r}
ta_draw_subset <- sample(unique(ta_em_draws$.draw), 200)

ta_em_draws_200 <- ta_em_draws  |>  
  filter(.draw %in% ta_draw_subset)
```

## Plot

```{r}
p2_ta_cover <- 
ta_em_draws_200 |> 
  ggplot(aes(x = Depth, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#929FBD", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "dodgerblue4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "dodgerblue4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0,0.75),
                     breaks = seq(0, 0.75, by = 0.25)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  ggtitle("Turfs") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18))
```

# OCTOCORAL

## Load model

```{r}
load("Model_Output/oct_mod.Rdata")
```

## Summary table

```{r}
oct_mod |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
 dplyr::select(matches("^b_.*|^bs.*|sds.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## Emmeans

```{r}
oct_em <- 
  oct_mod |> 
  emmeans(~ Depth,
          at = depth_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
oct_em_draws <- 
gather_emmeans_draws(oct_em)
```

## Subset 200 draws

```{r}
oct_draw_subset <- sample(unique(oct_em_draws$.draw), 200)

oct_em_draws_200 <- oct_em_draws  |>  
  filter(.draw %in% oct_draw_subset)
```

## Plot

```{r}
p4_oct_cover <- 
oct_em_draws_200 |> 
  ggplot(aes(x = Depth, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFB59E", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorange4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorange4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0,0.75),
                     breaks = seq(0, 0.75, by = 0.25)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  ggtitle("Octocoral") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18))
```

# SPONGE

## Load model

```{r}
load("Model_Output/sp_mod_glm.Rdata")
```

## Summary table

```{r}
sp_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
 dplyr::select(matches("^b_.*|^bs.*|sds.*"))  |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## Emmeans

```{r}
sp_em <- 
  sp_mod_glm |> 
  emmeans(~ Depth,
          at = depth_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
sp_em_draws <- 
gather_emmeans_draws(sp_em)
```

## Subset 200 draws

```{r}
sp_draw_subset <- sample(unique(sp_em_draws$.draw), 200)

sp_em_draws_200 <- sp_em_draws  |>  
  filter(.draw %in% sp_draw_subset)
```

## Plot

```{r}
p5_sp_cover <- 
sp_em_draws_200 |> 
  ggplot(aes(x = Depth, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#E29297", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "firebrick4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "firebrick4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "Proportional cover",
                     limits = c(0,0.75),
                     breaks = seq(0, 0.75, by = 0.25)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  ggtitle("Sponge") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# UNCONSOLIDATED SUBS

## Load model

```{r}
load("Model_Output/us_mod_glm.Rdata")
```

## Summary table

```{r}
us_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
 dplyr::select(matches("^b_.*|^bs.*|sds.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## Emmeans

```{r}
us_em <- 
  us_mod_glm |> 
  emmeans(~ Depth,
          at = depth_newdata,
          type = "response",
          epred = "TRUE") 
```

## Gather emmeans

```{r}
us_em_draws <- 
gather_emmeans_draws(us_em)
```

## Subset 200 draws

```{r}
us_draw_subset <- sample(unique(us_em_draws$.draw), 200)

us_em_draws_200 <- us_em_draws  |>  
  filter(.draw %in% us_draw_subset)
```

## Plot

```{r}
p6_us_cover <- 
us_em_draws_200 |> 
  ggplot(aes(x = Depth, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFAECF", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorchid4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorchid4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0,0.75),
                     breaks = seq(0, 0.75, by = 0.25)) +
  theme_classic() +
  scale_x_continuous(name = "Depth (m)") +
  ggtitle("Unconsolidated substrate") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# COMBINE PLOTS

```{r}
p_benthic_cover_depth <- 
(p3_hard_coral + p2_ta_cover) /
  (p5_sp_cover + p4_oct_cover) /
  (p1_ma + p6_us_cover) +
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

# ggsave

```{r}
ggsave("Figures/Fig. 2. V4_bc_depth.jpeg",
       plot = p_benthic_cover_depth, 
       dpi = 600, 
       height = 8.5, 
       width = 9, 
       units = "in")
```
