---
title: "benthic_model_plots"
format: html
editor: visual
---

# CORAL

## summary table

```{r}
coral_mod_glm |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

-   2% reduction in coral cover with increasing depth

## newdata

```{r}
depth_newdata <- with(benthic_v2,
                      data.frame(Depth = seq(min(Depth),
                                             max(Depth),
                                             length = 100)))
```

## predict coral cover

```{r}
coral_depth_pred <- coral_mod_glm |> 
  emmeans(~ Depth, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame() |> 
  mutate(p_cover = response * 100,
         p_cover_lower = lower.HPD * 100,
         p_cover_upper = upper.HPD * 100)
```

## plot coral cover

```{r}
p3_hard_coral <- 
coral_depth_pred |> 
  ggplot(aes(y = p_cover,
             x = Depth)) +
  geom_point(data = benthic_v2,
             aes(y = total_hard_coral),
             size = 2.5, 
             shape = 21,
             color = "#DDD487",
             fill = "#DDD487",
             alpha = 0.3) +
  geom_line(linewidth = 2, 
            color = "#DDD487") +
  geom_ribbon(aes(ymin = p_cover_lower,
                  ymax = p_cover_upper),
              fill = "#DDD487",
              color = "#DDD487",
              alpha = 0.6) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0, 100),
                     breaks = seq(0, 100, by = 25)) +
  scale_x_continuous(name = "") +
  ggtitle("Hard coral
P = 0.99") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# MACROALGAE

## summary table

```{r}
ma_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

-   Both GLM and GAM models suggest no changes in macroalgae with depth

## predict ma cover

```{r}
ma_depth_pred <- ma_mod_glm  |> 
  emmeans(~ Depth, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame() |> 
  mutate(p_cover = response * 100,
         p_cover_lower = lower.HPD * 100,
         p_cover_upper = upper.HPD * 100)
```

## plot ma cover

```{r}
p1_ma <- 
ma_depth_pred |> 
  ggplot(aes(y = p_cover,
             x = Depth)) +
  geom_point(data = benthic_v2,
             aes(y = total_macroalgae),
             size = 2.5, 
             shape = 21,
             color = "#8AA17D",
             fill = "#8AA17D",
             alpha = 0.3) +
  geom_line(linewidth = 2, 
            color = "#8AA17D") +
  geom_ribbon(aes(ymin = p_cover_lower,
                  ymax = p_cover_upper),
              fill = "#8AA17D",
              color = "#8AA17D",
              alpha = 0.6) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0, 100),
                     breaks = seq(0, 100, by = 25)) +
  scale_x_continuous(name = "") +
  ggtitle("Macroalgae
P = 0.71") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# TURF ALGAE

## summary table

```{r}
ta_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

-   \~ 2% change with depth

## predict ta cover

```{r}
ta_depth_pred <- ta_mod_glm |> 
  emmeans(~ Depth, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame() |> 
  mutate(p_cover = response * 100,
         p_cover_lower = lower.HPD * 100,
         p_cover_upper = upper.HPD * 100)
```

## plot ta cover

```{r}
p2_ta_cover <- 
ta_depth_pred |> 
  ggplot(aes(y = p_cover,
             x = Depth)) +
  geom_point(data = benthic_v2,
             aes(y = turf_algae),
             size = 2.5, 
             shape = 21,
             color = "#929FBD",
             fill = "#929FBD",
             alpha = 0.3) +
  geom_line(linewidth = 2, 
            color = "#929FBD") +
  geom_ribbon(aes(ymin = p_cover_lower,
                  ymax = p_cover_upper),
              fill = "#929FBD",
              color = "#929FBD",
              alpha = 0.6) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0, 100),
                     breaks = seq(0, 100, by = 25)) +
  scale_x_continuous(name = "") +
  ggtitle("Turf algae
P = 0.99") +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        #axis.title.y = element_text(size = 15),
        #axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# OCTOCORAL

## summary table

```{r}
oct_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict oct cover

```{r}
oct_depth_pred <- oct_mod_glm |> 
  emmeans(~ Depth, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame() |> 
  mutate(p_cover = response * 100,
         p_cover_lower = lower.HPD * 100,
         p_cover_upper = upper.HPD * 100)
```

## plot oct cover

```{r}
p4_oct_cover <- 
oct_depth_pred |> 
  ggplot(aes(y = p_cover,
             x = Depth)) +
  geom_point(data = benthic_v2,
             aes(y = total_octocoral),
             size = 2.5, 
             shape = 21,
             color = "#BFB59E",
             fill = "#BFB59E",
             alpha = 0.3) +
  geom_line(linewidth = 2, 
            color = "#BFB59E") +
  geom_ribbon(aes(ymin = p_cover_lower,
                  ymax = p_cover_upper),
              fill = "#BFB59E",
              color = "#BFB59E",
              alpha = 0.6) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0, 100),
                     breaks = seq(0, 100, by = 25)) +
  scale_x_continuous(name = "") +
  ggtitle("Octocoral
P = 1") +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        #axis.title.y = element_text(size = 15),
        #axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# ROCK

## summary table

```{r}
rock_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict rock cover

```{r}
rock_depth_pred <- rock_mod_glm |> 
  emmeans(~ Depth, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame() |> 
  mutate(p_cover = response * 100,
         p_cover_lower = lower.HPD * 100,
         p_cover_upper = upper.HPD * 100)
```

## plot rock cover

```{r}
p5_rock_cover <- 
rock_depth_pred |> 
  ggplot(aes(y = p_cover,
             x = Depth)) +
  geom_point(data = benthic_v2,
             aes(y = rock),
             size = 2.5, 
             shape = 21,
             color = "#E29297",
             fill = "#E29297",
             alpha = 0.3) +
  geom_line(linewidth = 2, 
            color = "#E29297") +
  geom_ribbon(aes(ymin = p_cover_lower,
                  ymax = p_cover_upper),
              fill = "#E29297",
              color = "#E29297",
              alpha = 0.6) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0, 100),
                     breaks = seq(0, 100, by = 25)) +
  scale_x_continuous(name = "Depth (m)") +
  ggtitle("Rock
P = 1") +
  theme_classic() +
  theme(
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# UNCONSILDATED SUBS

```{r}
us_mod_glm |> as_draws_df() |> 
  #dplyr::select(matches("^bs_.*")) |>
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1))
```

## predict us cover

```{r}
us_depth_pred <- us_mod_glm |> 
  emmeans(~ Depth, 
          at = depth_newdata, 
          type = "response") |> 
  as.data.frame() |> 
  mutate(p_cover = response * 100,
         p_cover_lower = lower.HPD * 100,
         p_cover_upper = upper.HPD * 100)
```

## plot us cover

```{r}
p6_us_cover <-
us_depth_pred |> 
  ggplot(aes(y = p_cover,
             x = Depth)) +
  geom_point(data = benthic_v2,
             aes(y = unconsolidated_subs),
             size = 2.5, 
             shape = 21,
             color = "#BFAECF",
             fill = "#BFAECF",
             alpha = 0.3) +
  geom_line(linewidth = 2, 
            color = "#BFAECF") +
  geom_ribbon(aes(ymin = p_cover_lower,
                  ymax = p_cover_upper),
              fill = "#BFAECF",
              color = "#BFAECF",
              alpha = 0.6) +
  scale_y_continuous(name = "Percentage cover",
                     limits = c(0, 100),
                     breaks = seq(0, 100, by = 25)) +
  scale_x_continuous(name = "Depth (m)") +
  ggtitle("Unconsolidated substrate
P = 0.56") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18))
```

# COMBINE PLOTS

```{r}
p_benthic_cover_depth <- 
(p1_ma + p2_ta_cover) /
  (p3_hard_coral + p4_oct_cover) /
  (p5_rock_cover + p6_us_cover)
```

-   Add images but this is okay for now

```{r}
ggsave("Fig. 2. bc_depth.jpeg",
       plot = p_benthic_cover_depth, 
       dpi = 600, 
       height = 8.5, 
       width = 8.5, 
       units = "in")
```
