---
title: "pred_fits"
format: html
editor: visual
---

# Description
This qmd examines the relationship between predator and herbivore abundance (total and for each feeding group).

# Clean up
```{r}
rm(list=ls())
gc()
```

# Library

```{r}
# load library
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(rstanarm)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(ggeffects)
library(broom.mixed)
library(bayestestR)
library(see)
library(easystats)
library(patchwork)
library(ggridges)
source("helperFunctions.R")
library(ggimage)
library(iNEXT)
set.seed(123)
```

Load csv

```{r}
preds <- read_csv("Data/db_predation.csv", trim_ws = TRUE)
```

## Select relevant variables

```{r}
preds_2 <-
  preds |> 
  select(Reef_2,
         Site.x,
         Transect,
         Number,
         Depth_m.x,
         cropper,
         browser,
         detritivore,
         excavator,
         scraper,
         total_herbs) |> 
  mutate(Reef_2 = factor(Reef_2),
         Site.x = factor(Site.x))
```

# TOTAL HERBIVORES

## Def formula

```{r}
pred_herbs_form <- bf(total_herbs ~ 
                   Number +
                   (1 | Reef_2/Site.x), 
                 family = zero_inflated_negbinomial())
```

## Weakly informed priors

```{r}
th_pred_priors <- prior(normal(2.2, 2.5), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2.5), class = "sd") +
  prior(beta(1,1), class = "zi") #+
  #prior(student_t(3, 0, 2.5), class = "sigma")
```

## Prior only model

```{r}
#| cache: true
th_pred_prior_mod <- brm(pred_herbs_form,
                    data = preds_2,
                    prior = th_pred_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Fit the model

```{r}
#| cache: true
th_pred_mod <- update(th_pred_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
th_pred_mod |> mcmc_plot(type = "trace")

# autocorr
th_pred_mod |> mcmc_plot(type = "acf_bar")

# rhat
th_pred_mod |> mcmc_plot(type = "rhat_hist")

# ess
th_pred_mod |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
th_pred_resids <- make_brms_dharma_res(th_pred_mod)

# qqplot
th_pred_resids |> testUniformity()

# residplot
th_pred_resids |> plotResiduals()

# testdisp
th_pred_resids |> testDispersion()
```

# Save model

```{r}
save(th_pred_mod, file = "Model/th_pred_mod.Rdata")
```

# CROPPERS

## Def formula

```{r}
pred_crop_form <- bf(cropper ~ 
                   Number +
                   (1 | Reef_2/Site.x), 
                 family = zero_inflated_negbinomial())
```

## Weakly informed priors

```{r}
crop_pred_priors <- prior(normal(1.6, 1.8), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1.8), class = "sd") +
  prior(beta(1,1), class = "zi") #+
  #prior(student_t(3, 0, 2.5), class = "sigma")
```

## Prior only model

```{r}
#| cache: true
crop_pred_prior_mod <- brm(pred_crop_form,
                    data = preds_2,
                    prior = crop_pred_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Fit the model

```{r}
#| cache: true
crop_pred_mod <- update(crop_pred_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
crop_pred_mod |> mcmc_plot(type = "trace")

# autocorr
crop_pred_mod |> mcmc_plot(type = "acf_bar")

# rhat
crop_pred_mod |> mcmc_plot(type = "rhat_hist")

# ess
crop_pred_mod |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
crop_pred_resids <- make_brms_dharma_res(crop_pred_mod)

# qqplot
crop_pred_resids |> testUniformity()

# residplot
crop_pred_resids |> plotResiduals()

# testdisp
crop_pred_resids |> testDispersion()
```

# Save model

```{r}
save(crop_pred_mod, file = "Model/crop_pred_mod.Rdata")
```

# DETRITIVORES

## Def formula

```{r}
pred_det_form <- bf(detritivore ~ 
                   Number +
                   (1 | Reef_2/Site.x), 
                 family = zero_inflated_negbinomial())
```

## Weakly informed priors

```{r}
det_pred_priors <- prior(normal(1.3, 1.7), class = "Intercept") +
  prior(normal(0, 0.8), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1.7), class = "sd") +
  prior(beta(1,1), class = "zi") #+
  #prior(student_t(3, 0, 2.5), class = "sigma")
```

## Prior only model

```{r}
#| cache: true
det_pred_prior_mod <- brm(pred_det_form,
                    data = preds_2,
                    prior = det_pred_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit the model

```{r}
#| cache: true
det_pred_mod <- update(det_pred_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
det_pred_mod |> mcmc_plot(type = "trace")

# autocorr
det_pred_mod|> mcmc_plot(type = "acf_bar")

# rhat
det_pred_mod |> mcmc_plot(type = "rhat_hist")

# ess
det_pred_mod |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
det_pred_resids <- make_brms_dharma_res(det_pred_mod)

# qqplot
det_pred_resids |> testUniformity()

# residplot
det_pred_resids |> plotResiduals()

# testdisp
det_pred_resids |> testDispersion()
```

# Save model

```{r}
save(det_pred_mod, file = "Model/det_pred_mod.Rdata")
```

# SCRAPERS

## Def formula

```{r}
pred_scra_form <- bf(scraper ~ 
                   Number +
                   (1 | Reef_2/Site.x), 
                 family = zero_inflated_negbinomial())
```

## Weakly informed priors

```{r}
scra_pred_priors <- prior(normal(0.5, 1.1), class = "Intercept") +
  prior(normal(0, 0.5), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 1.1), class = "sd") +
  prior(beta(1,1), class = "zi") #+
  #prior(student_t(3, 0, 2.5), class = "sigma")
```

## Prior only model

```{r}
#| cache: true
scra_pred_prior_mod <- brm(pred_scra_form,
                    data = preds_2,
                    prior = scra_pred_priors,
                    sample_prior = "only",
                    iter = 5000,
                    warmup = 1000,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

# Fit the model

```{r}
#| cache: true
scra_pred_mod <- update(scra_pred_prior_mod,
                  sample_prior = "yes",
                    iter = 10000,
                    warmup = 2000,
                    refresh = 2000)
```

## MCMC diagnostics

```{r}
# trace
scra_pred_mod |> mcmc_plot(type = "trace")

# autocorr
scra_pred_mod|> mcmc_plot(type = "acf_bar")

# rhat
scra_pred_mod |> mcmc_plot(type = "rhat_hist")

# ess
scra_pred_mod |> mcmc_plot(type = "neff_hist")
```

## Residuals

```{r}
scra_pred_resids <- make_brms_dharma_res(scra_pred_mod)

# qqplot
scra_pred_resids |> testUniformity()

# residplot
scra_pred_resids |> plotResiduals()

# testdisp
scra_pred_resids |> testDispersion()
```

# Save model

```{r}
save(scra_pred_mod, file = "Model/scra_pred_mod.Rdata")
```
