---
title: "Untitled"
format: html
editor: visual
---

# Description
This qmd has file has code on the interpretation and figure generation on the relationship between predator and herbivore abundance.

# LOAD models

```{r}
load("Model/th_pred_mod.Rdata")
load("Model/crop_pred_mod.Rdata")
load("Model/det_pred_mod.Rdata")
load("Model/scra_pred_mod.Rdata")
```

## Summary table

```{r}
scra_pred_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # exp to get log-odds scale (crosses 1)
  summarise_draws(median,
                  HDInterval::hdi, 
                  Pl= ~mean(.x < 1),
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 |
          Pg > 0.85)
```

Total predators: no effect (P = 0.52); 
Croppers: no effect (P = 0.79); 
Detritivores: no effect (P = 0.71);
Scrapers: no effect (P = 0.78)

# Plots

## Total herbivores

### Newdata

```{r}
predTH_newdata <- with(preds,
                         data.frame(Number = seq(min(Number),
                                          max(Number),
                                          length = 100)))
```

### Emmeans

```{r}
emmean_predTH <- 
  th_pred_mod |> 
  emmeans(~ Number,
          at = predTH_newdata,
          type = "response",
          epred = "TRUE") 
```

#### Gather emmeans

```{r}
predTH_draws <- 
gather_emmeans_draws(emmean_predTH)
```

#### Subset 200 draws

```{r}
predTH_draws_subset <- sample(unique(predTH_draws$.draw), 200)

predTH_draws_200 <- predTH_draws  |>  
  filter(.draw %in% predTH_draws_subset)
```

#### Plot: total herbivores

```{r}
p_predTH <- 
predTH_draws_200 |> 
  ggplot(aes(x = Number, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  ggtitle("Total herbivores")
```

## Croppers

### Emmeans

```{r}
emmean_predCROP <- 
  crop_pred_mod |> 
  emmeans(~ Number,
          at = predTH_newdata,
          type = "response",
          epred = "TRUE") 
```

#### Gather emmeans

```{r}
predCROP_draws <- 
gather_emmeans_draws(emmean_predCROP)
```

#### Subset 200 draws

```{r}
predCROP_draws_subset <- sample(unique(predCROP_draws$.draw), 200)

predCROP_draws_200 <- predCROP_draws  |>  
  filter(.draw %in% predCROP_draws_subset)
```

#### Plot: croppers

```{r}
p_predCROP <- 
predCROP_draws_200 |> 
  ggplot(aes(x = Number, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#BFB59E", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkorange4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkorange4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name = "",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(name = "") +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        #axis.ticks.x = element_blank(),
        #axis.title.y = element_text(size = 15),
        #axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  ggtitle("Croppers")
```

## Detritivores

### Emmeans

```{r}
emmean_predDET <- 
  det_pred_mod |> 
  emmeans(~ Number,
          at = predTH_newdata,
          type = "response",
          epred = "TRUE") 
```

#### Gather emmeans

```{r}
predDET_draws <- 
gather_emmeans_draws(emmean_predDET)
```

#### Subset 200 draws

```{r}
predDET_draws_subset <- sample(unique(predDET_draws$.draw), 200)

predDET_draws_200 <- predDET_draws  |>  
  filter(.draw %in% predDET_draws_subset)
```

#### Plot: detritivores

```{r}
predDET <- 
predDET_draws_200 |> 
  ggplot(aes(x = Number, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#929FBD", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "dodgerblue4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "dodgerblue4", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(expression(Abundance~(ind.150m^-2)),
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(expression(Predator~abundance~(ind.150m^-2))) +
  theme_classic() +
  theme(
        #axis.ticks.x = element_blank(),
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  ggtitle("Detritivores")
```

## Scrapers

### Emmeans

```{r}
emmean_predSCRA <- 
  scra_pred_mod |> 
  emmeans(~ Number,
          at = predTH_newdata,
          type = "response",
          epred = "TRUE") 
```

#### Gather emmeans

```{r}
predSCRA_draws <- 
gather_emmeans_draws(emmean_predSCRA)
```

#### Subset 200 draws

```{r}
predSCRA_draws_subset <- sample(unique(predSCRA_draws$.draw), 200)

predSCRA_draws_200 <- predSCRA_draws  |>  
  filter(.draw %in% predSCRA_draws_subset)
```

#### Plot: scrapers

```{r}
predSCRA <- 
predSCRA_draws_200 |> 
  ggplot(aes(x = Number, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#8AA17D", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "darkgreen", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "darkgreen", 
                  .width = 0.001, 
                  alpha = 1) +
  scale_y_continuous(name="",
                     limits = c(0,50),
                     breaks = seq(0, 50, by = 10)) +
  theme_classic() +
  scale_x_continuous(expression(Predator~abundance~(ind.150m^-2))) +
  theme_classic() +
  theme(
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 12),
        plot.title = element_text(size = 18)) +
  ggtitle("Scrapers")
```

# Combine plots

```{r}
p_predsCOMB <-
(p_predTH + p_predCROP) /
(predDET + predSCRA) +
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 15))
```

# ggsave

```{r}
ggsave("Figures/p_predsCOMB.jpeg",
       plot =p_predsCOMB, 
       dpi = 600, 
       height = 6.5, 
       width = 8, 
       units = "in")
```
